---
title: "import_clean_slim"
author: "Keith Hankowsky"
date: "3/28/2022"
output: html_document
---


```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(skimr)
library(data.table)
library(fuzzyjoin)
library(lubridate)
library(kableExtra)
library(geosphere)

library(maps) # land masses
library(rgdal) # read OGR vector maps into Spatial objects
library(viridis) # for customizing scale bars
library(mapproj)
library(hexbin)
library(sf)
library(scales)
library(beepr)
```


# Import Data
## Study fleet data
```{r}
#importing the study fleet data
study_fleet <- read_csv('./data/STUDY_FLEET_GROUNFISH_DATA_PULL_V1.csv')
```


## Observer data
```{r}
#reading in the data
observer1 <- read_excel("./data/22-029_Cadrin_OB.xlsx", sheet = 2, guess_max = 1048576)
observer2 <- read_excel("./data/22-029_Cadrin_OB.xlsx", sheet = 3, 
                        col_names = FALSE, guess_max = 1048576)

#taking the column titles from observer1 and applying them to observer2
observer_colnames <- as.vector(colnames(observer1))
names(observer2) <- observer_colnames

#binding the datasets together
observer <- bind_rows(observer1, observer2)

#changing the variables that need to be numeric 
observer <- observer %>%
  mutate(PROGRAM = as.numeric(PROGRAM), 
         PERMIT1 = as.numeric(PERMIT1), 
         HAULNUM = as.numeric(HAULNUM), 
         OBSRFLAG = as.numeric(OBSRFLAG), 
         YEARHBEG = as.numeric(YEARHBEG), 
         MONTHHBEG = as.numeric(MONTHHBEG), 
         DAYHBEG = as.numeric(DAYHBEG), 
         TIMEHBEG = as.numeric(TIMEHBEG), 
         TIMEHEND = as.numeric(TIMEHEND), 
         AREA = as.numeric(AREA), 
         NEGEAR = as.numeric(NEGEAR), 
         NETNAME = as.numeric(NETNAME), 
         NETTYPE = as.numeric(NETTYPE), 
         CODHUNG = as.numeric(CODHUNG), 
         LINERHUNG = as.numeric(LINERHUNG), 
         EXCLUSD = as.numeric(EXCLUSD), 
         EXCLTYP = as.numeric(EXCLTYP), 
         GRCABTYP = as.numeric(GRCABTYP), 
         BRDLGTYP = as.numeric(BRDLGTYP), 
         FTROPTYP = as.numeric(FTROPTYP), 
         CODLINERUSD = as.numeric(CODLINERUSD), 
         NESPP4 = as.numeric(NESPP4), 
         DRFLAG = as.numeric(DRFLAG), 
         CATDISP = as.numeric(CATDISP) , 
         FISHDISP = as.numeric(FISHDISP))



#fixing the issue with common_names 
observerA <- observer %>% slice_head(n = 1180571)
observerB <- observer %>% slice_tail(n = -1180571)


observerB <- observerB %>%
  mutate(COMNAME2 = MARKET, 
         MARKET = COMNAME, 
         COMNAME = COMNAME2) %>%
  select(-COMNAME2)


observer <- bind_rows(observerA, observerB)


#renaming these variable so it can be merged with the permit data
observer <- observer %>%
  mutate(YEAR = YEARHBEG,
         PERMIT = PERMIT1)


#import permit 
permit <- read_csv('./data/permit_output.csv')

#clean permit
permit_names <- permit %>% 
  names() %>% 
  str_squish() %>%
  str_split(., pattern = " ")

permit <- permit %>% 
  mutate_all(str_squish) %>% 
  separate(1, into = permit_names[[1]], sep = " ") %>% 
  mutate_all(as.numeric)


#join observer and permit data 
observer <- left_join(observer, permit, by = c("YEAR", "PERMIT"), all.x = TRUE, no.dups = TRUE)


#clear environment of unnecessary datasets
rm(observer1)
rm(observer2)
rm(permit)
rm(permit_names)

```


## NEFSC survey data
```{r}
#importing and joining the spring nefsc survey catch and station data and joining them 
nefsc_station_spring <- read_csv('./data/22561_UNION_FSCS_SVSTA_spring.csv')

nefsc_catch_spring <- read_csv('./data/22561_UNION_FSCS_SVCAT_spring.csv')

nefsc_spring <- left_join(nefsc_station_spring, nefsc_catch_spring, 
                           by = c("ID", "CRUISE6", "STRATUM", "TOW", "STATION"))


#importing and joining the fall nefsc survey catch and station data and joining them 
nefsc_station_fall <- read_csv('./data/22560_UNION_FSCS_SVSTA_fall.csv')

nefsc_catch_fall <- read_csv('./data/22560_UNION_FSCS_SVCAT_fall.csv')
  
nefsc_fall <- left_join(nefsc_station_fall, nefsc_catch_fall, 
                           by = c("ID", "CRUISE6", "STRATUM", "TOW", "STATION"))


#joining the spring and fall survey datasets 
nefsc <- rbind(nefsc_spring, nefsc_fall)





#assigning commercial selectivity to the NEFSC trawl survey based on minimum fish size
#import the spring length data
nefsc_length_spring <- read_csv("./data/22561_UNION_FSCS_SVLEN_spring.csv", 
                                col_types = list(
                                  CRUISE6 = col_double(),
                                  STRATUM = col_double(),
                                  TOW = col_double(),
                                  STATION = col_double(),
                                  ID = col_double(),
                                  LOGGED_SPECIES_NAME = col_character(),
                                  SVSPP = col_double(),
                                  CATCHSEX = col_double(),
                                  LENGTH = col_double(),
                                  EXPNUMLEN = col_double()))

#the goal here is to select the individuals smaller than commercial selectivity
#and apply a length-weight relationship to get their estimated weight and then 
#subtract that from the aggregate catch weight 

#filtering for species of interest and above their minimum landing size
nefsc_length_spring_select <- nefsc_length_spring %>%
  filter(SVSPP %in% c(73, 74, 75, 107, 105, 102, 101, 106, 155, 197)) %>%
  filter(SVSPP == 73 & LENGTH < 48.26 | #cod, minimum size 19in (48.26cm)
           SVSPP == 74 & LENGTH < 40.64 | #haddock, minimum size 16in (40.64cm)
           SVSPP == 75 & LENGTH < 48.26 | #pollock, minimum size 19in (48.26cm)
           SVSPP == 107 & LENGTH < 33.03 | #witch flounder, minimum size 13in (33.03cm)
           SVSPP == 105 & LENGTH < 30.38 | #yellowtail flounder, minimum size 12in (30.48cm)
           SVSPP == 102 & LENGTH < 30.38 | #american plaice, minimum size 12in (30.48cm)
           SVSPP == 101 & LENGTH < 104.14 | #atlantic halibut, minimum size 41in (104.14cm)
           SVSPP == 106 & LENGTH < 30.38 | #winter flounder, minimum size 12in (30.48cm)
           SVSPP == 155 & LENGTH < 17.78 | #acadian redfish, minimum size 7in (17.78cm)   #NE Groundfish spp
           SVSPP == 197 & LENGTH < 43.81 #goosefish, minimum size 17in (43.81cm) for whole fish or 11in for tails only 
           )



#applying the length-weight relationship to the spring survey data 
#length-weight parameters were obtained from Wigley et al (2003)
nefsc_length_spring_select <- nefsc_length_spring_select %>%
  mutate(ln_L = log(LENGTH)) %>%
  mutate(ln_a = case_when(
    SVSPP == 73 ~ -11.7803, 
    SVSPP == 74 ~ -11.8062, 
    SVSPP == 107 ~ -13.2151, 
    SVSPP == 105 ~ -12.3581, 
    SVSPP == 102 ~ -12.8117, 
    SVSPP == 106 ~ -11.4718, 
    SVSPP == 197 ~ -10.7668)) %>%
  mutate(b = case_when(
    SVSPP == 73 ~ 3.0606, 
    SVSPP == 74 ~ 3.0766, 
    SVSPP == 107 ~ 3.3289, 
    SVSPP == 105 ~ 3.2099, 
    SVSPP == 102 ~ 3.3125, 
    SVSPP == 106 ~ 3.0431, 
    SVSPP == 197 ~ 2.9302)) %>%
  mutate(ln_W = ln_a + (b*ln_L)) %>%
  mutate(Weight = exp(ln_W)) %>% 
  mutate(totalWeight = Weight*EXPNUMLEN) %>%
  group_by(CRUISE6, STRATUM, TOW, STATION, ID, SVSPP) %>%
  summarise(undersized_fish_WT = sum(Weight)) %>%
  ungroup() %>%
  drop_na(undersized_fish_WT) 


#updating SVSPP variable to be consistent across datasets for the merge
nefsc_catch_spring <- nefsc_catch_spring %>%
  mutate(SVSPP = as.numeric(SVSPP))


#join the undersized fish data (length + weight) with the aggregate catch data
nefsc_catch_spring_updated <- full_join(nefsc_catch_spring, nefsc_length_spring_select, 
                                        by = c("CRUISE6", "STRATUM", "TOW", "STATION", "SVSPP"))


#subtracting the small fish from the total weight at each station for each species 
nefsc_catch_spring_updated <- nefsc_catch_spring_updated %>%
  mutate(undersized_fish_WT = ifelse(is.na(undersized_fish_WT), 0, undersized_fish_WT)) %>%
  mutate(CATCHWT_updated = EXPCATCHWT - undersized_fish_WT) %>%
  mutate(CATCHWT_updated = ifelse(CATCHWT_updated <0, 0 , CATCHWT_updated))


#joining the updated spring catch data with the spring station data
nefsc_spring_updated <- left_join(nefsc_station_spring, nefsc_catch_spring_updated, 
                           by = c("CRUISE6", "STRATUM", "TOW", "STATION"))



#SAME THING BUT FOR FALL SURVEY 
#import the fall length data
nefsc_length_fall <- read_csv("./data/22560_UNION_FSCS_SVLEN_fall.csv", 
                                col_types = list(
                                  CRUISE6 = col_double(),
                                  STRATUM = col_double(),
                                  TOW = col_double(),
                                  STATION = col_double(),
                                  ID = col_double(),
                                  LOGGED_SPECIES_NAME = col_character(),
                                  SVSPP = col_double(),
                                  CATCHSEX = col_double(),
                                  LENGTH = col_double(),
                                  EXPNUMLEN = col_double()))

#filtering for species of interest and below their minimum landing size
nefsc_length_fall_select <- nefsc_length_fall %>%
  filter(SVSPP %in% c(73, 74, 75, 107, 105, 102, 101, 106, 155, 197)) %>%
  filter(SVSPP == 73 & LENGTH < 48.26 | #cod, minimum size 19in (48.26cm)
           SVSPP == 74 & LENGTH < 40.64 | #haddock, minimum size 16in (40.64cm)
           SVSPP == 75 & LENGTH < 48.26 | #pollock, minimum size 19in (48.26cm)
           SVSPP == 107 & LENGTH < 33.03 | #witch flounder, minimum size 13in (33.03cm)
           SVSPP == 105 & LENGTH < 30.38 | #yellowtail flounder, minimum size 12in (30.48cm)
           SVSPP == 102 & LENGTH < 30.38 | #american plaice, minimum size 12in (30.48cm)
           SVSPP == 101 & LENGTH < 104.14 | #atlantic halibut, minimum size 41in (104.14cm)
           SVSPP == 106 & LENGTH < 30.38 | #winter flounder, minimum size 12in (30.48cm)
           SVSPP == 155 & LENGTH < 17.78 | #acadian redfish, minimum size 7in (17.78cm)   #NE Groundfish spp
           SVSPP == 197 & LENGTH < 43.81 #goosefish, minimum size 17in (43.81cm) for whole fish or 11in 
                                                    #for tails only 
           )

#applying the length-weight relationship to the fall survey data 
nefsc_length_fall_select <- nefsc_length_fall_select %>%
  mutate(ln_L = log(LENGTH)) %>%
  mutate(ln_a = case_when(
    SVSPP == 73 ~ -11.9920, 
    SVSPP == 74 ~ -11.8111, 
    SVSPP == 107 ~ -12.7334, 
    SVSPP == 105 ~ -11.8381, 
    SVSPP == 102 ~ -12.7492, 
    SVSPP == 106 ~ -11.6356, 
    SVSPP == 197 ~ -10.7106)) %>%
  mutate(b = case_when(
    SVSPP == 73 ~ 3.1262, 
    SVSPP == 74 ~ 3.0888, 
    SVSPP == 107 ~ 3.1997, 
    SVSPP == 105 ~ 3.0559, 
    SVSPP == 102 ~ 3.3062, 
    SVSPP == 106 ~ 3.1091, 
    SVSPP == 197 ~ 2.9227)) %>%
  mutate(ln_W = ln_a + (b*ln_L)) %>%
  mutate(Weight = exp(ln_W)) %>% 
  mutate(totalWeight = Weight*EXPNUMLEN) %>%
  group_by(CRUISE6, STRATUM, TOW, STATION, ID, SVSPP) %>%
  summarise(undersized_fish_WT = sum(Weight)) %>%
  ungroup() %>%
  drop_na(undersized_fish_WT)

#updating SVSPP variable to be consistent across datasets for the merge
nefsc_catch_fall <- nefsc_catch_fall %>%
  mutate(SVSPP = as.numeric(SVSPP))

#join the undersized fish data (length + weight) with the aggregate catch data
nefsc_catch_fall_updated <- full_join(nefsc_catch_fall, nefsc_length_fall_select, 
                                        by = c("CRUISE6", "STRATUM", "TOW", "STATION", "SVSPP"))

#subtracting the small fish from the total weight at each station for each species 
nefsc_catch_fall_updated <- nefsc_catch_fall_updated %>%
  mutate(undersized_fish_WT = ifelse(is.na(undersized_fish_WT), 0, undersized_fish_WT)) %>%
  mutate(CATCHWT_updated = EXPCATCHWT - undersized_fish_WT) %>%
  mutate(CATCHWT_updated = ifelse(CATCHWT_updated <0, 0 , CATCHWT_updated))

#joining the updated fall catch data with the fall station data
nefsc_fall_updated <- left_join(nefsc_station_fall, nefsc_catch_fall_updated, 
                           by = c("CRUISE6", "STRATUM", "TOW", "STATION"))



#joining the updated spring and fall survey datasets 
nefsc <- rbind(nefsc_spring_updated, nefsc_fall_updated)




#reading in the NEFSC survey swept area data
nefsc_netdata <- read_csv("./data/Hankowksy_tow_eval_data_2009_2022.csv")

#clean the NEFSC survey net data 
netdata_names <- nefsc_netdata %>%
  names() %>%
  str_split(., pattern = ",")

nefsc_netdata <- nefsc_netdata %>%
  separate(1, into = netdata_names[[1]], sep = ",") 

nefsc_netdata <- nefsc_netdata %>%
  mutate(CRUISE6 = as.numeric(as.character(CRUISE6))) %>%
  mutate(STATION = as.numeric(STATION)) %>%
  mutate(STRATUM = as.numeric(STRATUM)) %>%
  mutate(TOW = as.numeric(TOW)) %>%
  mutate(AREA_SWEPT_DOORS_MEAN_KM2 = as.numeric(AREA_SWEPT_DOORS_MEAN_KM2)) %>%
  mutate(AREA_SWEPT_WINGS_MEAN_KM2 = as.numeric(AREA_SWEPT_WINGS_MEAN_KM2)) %>%
  select(CRUISE6, STATION, STRATUM, TOW, AREA_SWEPT_DOORS_MEAN_KM2, AREA_SWEPT_WINGS_MEAN_KM2)

#joining the net mensuration data with the full nefsc data 
nefsc <- left_join(nefsc, nefsc_netdata, by = c("CRUISE6", "STRATUM", "TOW", "STATION"))




rm(nefsc_station_spring)
rm(nefsc_catch_spring)
rm(nefsc_spring)
rm(nefsc_station_fall)
rm(nefsc_catch_fall)
rm(nefsc_fall)
```


## VW Trawl Data 
```{r}
# #importing and joining the 2019 VW survey catch and station data and joining them 
# vw_station_2019 <- read_csv('./data/VW_2019-2020_Tow_Info.csv')
# 
# vw_catch_2019 <- read_csv('./data/VW_2019-2020_WeightTable.csv')
# 
# vw_2019 <- left_join(vw_station_2019, vw_catch_2019, 
#                            by = c("TowID"))
# 
# 
# #importing and joining the 2020 VW survey catch and station data and joining them 
# vw_station_2020 <- read_csv('./data/VW_2020-2021_TowInfo.csv')
# 
# vw_catch_2020 <- read_csv('./data/VW_2020-2021_WeightTable.csv')
# 
# vw_2020 <- left_join(vw_station_2020, vw_catch_2020, 
#                            by = c("TowID"))
# 
# 
# #joining the 2019 and 2020 survey datasets 
# vw <- rbind(vw_2019, vw_2020)
# 
# 
# #adding common species name column 
# vw <- vw %>%
#   mutate(common_name = case_when(
#     SpeciesID == 10 ~ "Alewife", 
#     SpeciesID == 124	~ "Monkfish",
#     SpeciesID == 230	~ "Bluefish",
#     SpeciesID == 511	~ "Butterfish",
#     SpeciesID == 818	~ "Atlantic Cod",
#     SpeciesID == 900	~ "Atlantic Croaker",
#     SpeciesID == 930	~ "Cunner",
#     SpeciesID == 960	~ "Cusk",
#     SpeciesID == 1120	~ "Herring, Blueback",
#     SpeciesID == 1150	~ "American Eel",
#     SpeciesID == 1160  ~ "Eel, Conger",
#     SpeciesID == 1200	~ "Flounder, Winter",
#     SpeciesID == 1219	~ "Flounder, Summer (Fluke)",
#     SpeciesID == 1220	~ "Flounder, Witch",
#     SpeciesID == 1230	~ "Flounder, Yellowtail",
#     SpeciesID == 1240	~ "Flounder, American Plaice",
#     SpeciesID == 1250	~ "Flounder, Windowpane",
#     SpeciesID == 1270	~ "Flounder, Fourspot",
#     SpeciesID == 1290	~ "Flounder, Gulfstream",
#     SpeciesID == 1300	~ "Flounder, Southern",
#     SpeciesID == 1477	~ "Haddock",
#     SpeciesID == 1520	~ "Hake, Red",
#     SpeciesID == 1539	~ "Hake, White",
#     SpeciesID == 1590	~ "Atlantic Halibut",
#     SpeciesID == 1685	~ "Herring, Atlantic",
#     SpeciesID == 2120	~ "Mackerel, Atlantic",
#     SpeciesID == 2210	~ "Menhaden, Atlantic",
#     SpeciesID == 2400	~ "Redfish",
#     SpeciesID == 2500	~ "Ocean Pout",
#     SpeciesID == 2695	~ "Pollock",
#     SpeciesID == 3270	~ "Sea Raven",
#     SpeciesID == 3295	~ "Scup",
#     SpeciesID == 3350	~ "Black Sea bass",
#     SpeciesID == 3400	~ "Sea Robin, Northern",
#     SpeciesID == 3420	~ "Sea Robin, Striped",
#     SpeciesID == 3446	~ "Weakfish",
#     SpeciesID == 3474	~ "Shad, American",
#     SpeciesID == 3511	~ "Dogfish, Smooth",
#     SpeciesID == 3521	~ "Dogfish, Spiny",
#     SpeciesID == 3531	~ "Shark, Thresher",
#     SpeciesID == 3610	~ "Capelin",
#     SpeciesID == 3650	~ "Skate, Mixed",
#     SpeciesID == 3660	~ "Skate, Little",
#     SpeciesID == 3670	~ "Skate, Winter",
#     SpeciesID == 3680	~ "Skate, Barndoor",
#     SpeciesID == 3690	~ "Skate, Smooth",
#     SpeciesID == 3700	~ "Skate, Thorny",
#     SpeciesID == 3720	~ "Skate, Clearnose",
#     SpeciesID == 4180	~ "Striped Bass",
#     SpeciesID == 4380	~ "Tautog",
#     SpeciesID == 4811	~ "Shark, Porbeagle",
#     SpeciesID == 4931	~ "Shark, Blue",
#     SpeciesID == 5090	~ "Hake, Silver",
#     SpeciesID == 5120	~ "Wolffish",
#     SpeciesID == 6602	~ "Hake, Spotted",
#     SpeciesID == 6616	~ "Kingfish, Northern",
#     SpeciesID == 6640	~ "Cutlassfish, Atlantic",
#     SpeciesID == 6678	~ "Sculpin, Longhorn",
#     SpeciesID == 6790	~ "Wrymouth",
#     SpeciesID == 6870	~ "Snail, Moonshell",
#     SpeciesID == 7120	~ "Crab, Cancer",
#     SpeciesID == 7270	~ "Lobster, American",
#     SpeciesID == 7360	~ "Northern Shrimp",
#     SpeciesID == 7690	~ "Clam, Surf",
#     SpeciesID == 8009	~ "Sea Scallop",
#     SpeciesID == 8010	~ "Squid, Atlantic Longfin",
#     SpeciesID == 8020	~ "Squid, Shortfin")) %>%
#   relocate(common_name, .after = SpeciesID)
# 
# 
# 
# rm(vw_station_2019)
# rm(vw_catch_2019)
# rm(vw_station_2020)
# rm(vw_catch_2020)
# rm(vw_2019)
# rm(vw_2020)
```


# Filtering
## Filtering datasets for just trawl gears and after 2009
```{r}
#filtering the study fleet dataset to include only trawl gears and only after 2009
sf_trawl <- study_fleet %>%
  filter(VTR_GEAR_CODE %in% c('OHS', 'OTF', 'OTO', 'OTR')) %>%
      #OHS - otter trawl, haddock separator
      #OTF - otter trawl, bottom, fish 
      #OTM - otter trawl, midwater
      #OTO - otter trawl, bottom, other
      #OTR - otter trawl, ruhle 
      #OTS - otter trawl, bottom, shrimp
  filter(YEAR >= 2009) %>%
  mutate(survey_comercial_ID = 2) %>%
  rename(START_TOW_DATE_GMT = START_HAUL_DATE_GMT) %>%
  rename(END_TOW_DATE_GMT = END_SET_DATE_GMT) %>%
  rename(START_TOW_LAT = START_HAUL_LAT) %>% 
  rename(START_TOW_LON = START_HAUL_LON) %>%
  rename(END_TOW_LAT = END_SET_LAT) %>%
  rename(END_TOW_LON = END_SET_LON) %>%
  rename(trawl_type = VTR_GEAR_CODE) %>%
  drop_na(END_TOW_LAT) %>%
  drop_na(END_TOW_LON)

#calculating haul duration and distance because the ones from NOAA have NAs and don't seem accurate
sf_trawl <- sf_trawl %>% 
  mutate(haul_dur = START_TOW_DATE_GMT - END_TOW_DATE_GMT) %>%
  mutate(haul_dur_hr = (as.numeric(haul_dur)/60)/60) %>%
  mutate(haul_dist_nm = (distHaversine(cbind(START_TOW_LON, START_TOW_LAT), cbind(END_TOW_LON, END_TOW_LAT)))/1852)
  
  

#filter the observer data set to include only trawl gears and only after 2009
observer_trawl <- observer %>%
  filter(NEGEAR %in% c(050, 057, 150)) %>%
      #050 - Trawl, Otter, Bottom, Fish
      #057 - Trawl, Otter, Bottom, Haddock Separator
      #150 - Trawl, Otter, Bottom, Large Mesh Belly Panel
  mutate(trip_haul_ID = paste(TRIPID,HAULNUM, sep = '_')) %>%
  relocate(trip_haul_ID) %>%
  filter(YEARHBEG  >= 2009) %>%
  mutate(survey_comercial_ID = 3) %>%
  rename(START_TOW_LAT = GIS_LATHBEG) %>% 
  rename(START_TOW_LON = GIS_LONHBEG) %>%
  rename(END_TOW_LAT = GIS_LATHEND) %>%
  rename(END_TOW_LON = GIS_LONHEND) %>%
  drop_na(END_TOW_LAT) %>%
  drop_na(END_TOW_LON)
  # drop_na(LENGTH)
  # rename(END_TOW_DATE_GMT = END_SET_DATE_GMT) %>%
    #no end date information in the observer dataset 
  
  
#filtering the nefsc survey dataset to only after 2009 because of the shift to the bigelow 
nefsc <- nefsc %>%
  mutate(cruise_station_ID = paste(CRUISE6,STATION, sep = '_')) %>%
  relocate(cruise_station_ID) %>%
  filter(EST_YEAR >= 2009) %>%
  mutate(BEGIN_EST_TOWDATE = as.POSIXct(BEGIN_EST_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
  mutate(END_EST_TOWDATE = as.POSIXct(END_EST_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
  mutate(BEGIN_GMT_TOWDATE = as.POSIXct(BEGIN_GMT_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
  mutate(END_GMT_TOWDATE = as.POSIXct(END_GMT_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
  mutate(survey_commerical_ID = 1) %>%
  rename(START_TOW_DATE_GMT = BEGIN_GMT_TOWDATE) %>%
  rename(END_TOW_DATE_GMT = END_GMT_TOWDATE) %>%
  rename(START_TOW_LAT = DECDEG_BEGLAT) %>%
  rename(START_TOW_LON = DECDEG_BEGLON) %>%
  rename(END_TOW_LAT = DECDEG_ENDLAT) %>%
  rename(END_TOW_LON = DECDEG_ENDLON) %>%
  drop_na(END_TOW_LAT) %>%
  drop_na(END_TOW_LON)



#filtering the VW survey dataset - creating datetime columns and cleaning lat/long columns
# vw <- vw %>%
#   mutate(START_TOW_DATE = as.POSIXct(paste(TripDate, TowStartTime), format = "%m/%d/%y %H:%M", tz = "EST")) %>%
#   mutate(END_TOW_DATE = as.POSIXct(paste(TripDate, TowEndTime), format = "%m/%d/%y %H:%M", tz = "EST")) %>%
#   mutate(START_TOW_DATE_GMT = with_tz(START_TOW_DATE, "GMT")) %>%
#   mutate(END_TOW_DATE_GMT = with_tz(END_TOW_DATE, "GMT")) %>%
#   relocate(START_TOW_DATE, .after = TowStartTime) %>%
#   relocate(START_TOW_DATE_GMT, .after = START_TOW_DATE) %>%
#   relocate(END_TOW_DATE, .after = TowEndTime) %>%
#   relocate(END_TOW_DATE_GMT, .after = END_TOW_DATE) %>%
#   mutate_at(c("TowStartLat", "TowEndLat"), str_remove, "N ") %>%
#   mutate_at(c("TowStartLong", "TowEndLong"), str_replace, "W ", "-") %>%
#   mutate_at(c("TowStartLat", "TowEndLat", "TowStartLong", "TowEndLong"), str_replace, "(?<=\\.\\d\\d)\\.", "") %>%
#   mutate(TotalWeight_lb = TotalWeight_kg*2.2046226218) %>%
#   rename(START_TOW_LAT = TowStartLat) %>%
#   rename(START_TOW_LON = TowStartLong) %>%
#   rename(END_TOW_LAT = TowEndLat) %>%
#   rename(END_TOW_LON = TowEndLong) %>%
#   mutate(across(c("START_TOW_LAT", "START_TOW_LON", "END_TOW_LAT", "END_TOW_LON"), as.double))
# 
# 



rm(study_fleet)
rm(observer)
```



## Assigning NEFSC Survey Strata to Commercial Tows 
```{r}
#Assigning NEFSC survey strata to commercial Study Fleet tows 
#read in the nefsc survey strata data
sf::sf_use_s2(FALSE)
nefsc_strata <- st_read(dsn = "./data/strata") %>%
  st_set_crs(4269)

st_make_valid(nefsc_strata)

#creating a midpoint variable of the tow and using that as the determining criteria
sf_trawl <- sf_trawl %>%
  drop_na(c(START_TOW_LAT, END_TOW_LAT, START_TOW_LON, END_TOW_LON)) %>%
  mutate(midpoint_lat = rowMeans(across(c(START_TOW_LAT, END_TOW_LAT)))) %>%
  mutate(midpoint_long = rowMeans(across(c(START_TOW_LON, END_TOW_LON))))

#selecting just the midpoint values because the geometry field will not be created correctly with all the other variables in the dataset
sf_points <- sf_trawl %>%  
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  select(midpoint_lat, midpoint_long)

#turning the lat/long variables into an sf feature 
sf_points_sf <- st_as_sf(sf_points, coords = c("midpoint_long", "midpoint_lat"), 
                             crs = st_crs(nefsc_strata))

#running the actual intersection of the tows in the strata and creating a column in the points dataset specifying which stratum the tows occurred in 
sf_points$strata <- apply(st_contains(nefsc_strata, sf_points_sf, sparse = FALSE), 2, 
               function(col) { 
                  nefsc_strata[which(col), ]$STRATA
               })

#changing the strata column to numeric instead of a list 
sf_points <- sf_points %>%
  mutate(strata = as.numeric(strata))

#left joining the points dataset (with the stratum column) to the OG study fleet trawl dataset by the lat/long columns
sf_trawl <- left_join(sf_trawl, sf_points, by = c("midpoint_lat", "midpoint_long"))


################################################################################


#Assigning NEFSC survey strata to commercial Observer tows 
#creating a midpoint variable of the tow and using that as the determining criteria
observer_trawl <- observer_trawl %>%
  drop_na(c(START_TOW_LAT, END_TOW_LAT, START_TOW_LON, END_TOW_LON)) %>%
  mutate(midpoint_lat = rowMeans(across(c(START_TOW_LAT, END_TOW_LAT)))) %>%
  mutate(midpoint_long = rowMeans(across(c(START_TOW_LON, END_TOW_LON))))

#selecting just the midpoint values because the geometry field will not be created correctly with all the other variables in the dataset
ob_points <- observer_trawl %>%  
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  select(midpoint_lat, midpoint_long)

#turning the lat/long variables into an sf feature 
ob_points_sf <- st_as_sf(ob_points, coords = c("midpoint_long", "midpoint_lat"), 
                             crs = st_crs(nefsc_strata))

#running the actual intersection of the tows in the strata and creating a column in the points dataset specifying which stratum the tows occured in 
ob_points$strata <- apply(st_contains(nefsc_strata, ob_points_sf, sparse = FALSE), 2, 
               function(col) { 
                  nefsc_strata[which(col), ]$STRATA
               })

#changing the strata column to numeric instead of a list 
ob_points <- ob_points %>%
  mutate(strata = as.numeric(strata))

#left joining the points dataset (with the stratum column) to the OG study fleet trawl dataset by the lat/long columns
observer_trawl <- left_join(observer_trawl, ob_points, by = c("midpoint_lat", "midpoint_long"))




rm(sf_points)
rm(sf_points_sf)
rm(ob_points)
rm(ob_points_sf)
```



## Estimating Swept Area
```{r}
#All of this is taken from 'FISHING EFFECTS MODEL NORTHEAST REGION - NEFMC (2019)' APPENDIX A 

###############################################################################################################
####################################Swept area for Study Fleet Hauls ########################################
# DISTANCE
sf_trawl$d_t <- sf_trawl$haul_dist_nm * 1.852 # Distance towed (kilometers)



# BOARDS Weight of otter trawl doors estimated by regression
sf_trawl$weight <- 70.848 + (1.844 * sf_trawl$GTONS) + (0.5344 * sf_trawl$VHP)
# Width trawl doors (meters) estimated by regression
sf_trawl$width_o <- 0.001 * (1223 + (sf_trawl$weight * 0.8333))
# Angle of attack (radians)
sf_trawl$rad_o <- (2 * pi * 40)/360
# Effective Width of otter board (meters)
sf_trawl$w_o <- sf_trawl$width_o * sin(sf_trawl$rad_o)
# Contact index for otter boards is constant
sf_trawl$c_o <- 1



# CABLES (contact index set below) Width of ground cable (meters) based on regression
sf_trawl$width_c <- 0.3048 * (137.54 + (sf_trawl$LEN * 1.823))
# Angle of attack (radians) of ground cable
sf_trawl$rad_c <- (2 * pi * 15)/360
# Effective width of ground cable (meters)
sf_trawl$w_c <- sf_trawl$width_c * sin(sf_trawl$rad_c)



# SWEEP (contact index set below)
sf_trawl$raw_sweep <- sf_trawl$GEAR_SIZE
sf_trawl$w_s <- 0.43 * sf_trawl$raw_sweep # Effective width of sweep (meters)



# CONTACT INDECIES 
sf_trawl$c_c <- 0.95 #CABLES
sf_trawl$c_s <- 0.9  #SWEEP



sf_trawl$boards <- 2 * sf_trawl$w_o * sf_trawl$c_o # Width of both boards (meters)
sf_trawl$cables <- 2 * sf_trawl$w_c * sf_trawl$c_c # Width of both cables (meters)
sf_trawl$sweep <- sf_trawl$w_s * sf_trawl$c_s # Width of the sweep (meters)
sf_trawl$lin_eff_width <- sf_trawl$boards + sf_trawl$cables + sf_trawl$sweep
sf_trawl$swept_area <- sf_trawl$d_t * (0.001 * sf_trawl$lin_eff_width) # SA without sensitivity (km)



###############################################################################################################
####################################Swept area for Observer Hauls ########################################
# DISTANCE
    #Using the towspeed from the observer dataset. however if there is an NA in the observer datasets, setting the towspeed to 3 in accordance with the 'FISHING EFFECTS MODEL NORTHEAST REGION - NEFMC (2019)'
observer_trawl$towspeed <- ifelse(is.na(observer_trawl$TOWSPEED), 3, observer_trawl$TOWSPEED) # Towspeed (Nautical Miles/Hr)
observer_trawl$hours_fished <- observer_trawl$HAULDUR # Total hours fished
observer_trawl$d_nm <- observer_trawl$towspeed * observer_trawl$hours_fished # Distance (Nautical Miles)
observer_trawl$d_t <- observer_trawl$d_nm * 1.852 # Distance towed (kilometers)



# BOARDS Weight of otter trawl doors estimated by regression
    #Using the doorweight from the observer dataset. However if there is an NA in the observer dataset, calculating the doorweight based on the tonnange and vessel horsepower from the permit data in accordance with the FISHING EFFECTS MODEL NORTHEAST REGION - NEFMC (2019)'
observer_trawl$weight <- ifelse(is.na(observer_trawl$DOORWGT), 70.848 + (1.844 * observer_trawl$GTONS) + (0.5344 * observer_trawl$VHP), observer_trawl$DOORWGT)
# Width trawl doors (meters) estimated by regression
observer_trawl$width_o <- 0.001 * (1223 + (observer_trawl$weight * 0.8333))
# Angle of attack (radians)
observer_trawl$rad_o <- (2 * pi * 40)/360
# Effective Width of otter board (meters)
observer_trawl$w_o <- observer_trawl$width_o * sin(observer_trawl$rad_o)
# Contact index for otter boards is constant
observer_trawl$c_o <- 1
# 
# 
# 
# CABLES (contact index set below) Width of ground cable (meters) based on regression
    #Using the ground_cable_length from the observer dataset. However if there is an NA in the observer dataset, calculating the ground_cable_length based on the vessel length from the permit data in accordance with the FISHING EFFECTS MODEL NORTHEAST REGION - NEFMC (2019)'
observer_trawl$length_c <- ifelse(is.na(observer_trawl$GRCABLEN), (23.3 + (0.4*(observer_trawl$LENGTH*0.3048))), (observer_trawl$GRCABLEN))
#Going from ground cable length to ground cable width
observer_trawl$width_c <- 0.3048 * (137.54 + (observer_trawl$length_c * 1.823))
# Angle of attack (radians) of ground cable
observer_trawl$rad_c <- (2 * pi * 15)/360
# Effective width of ground cable (meters)
observer_trawl$w_c <- observer_trawl$length_c * sin(observer_trawl$rad_c)



# SWEEP (contact index set below)
observer_trawl$raw_sweep <- observer_trawl$FTROPLEN
observer_trawl$w_s <- 0.43 * observer_trawl$raw_sweep # Effective width of sweep (meters)



# CONTACT INDECIES
observer_trawl$c_c <- 0.95 #CABLES
observer_trawl$c_s <- 0.9  #SWEEP



observer_trawl$boards <- 2 * observer_trawl$w_o * observer_trawl$c_o # Width of both boards (meters)
observer_trawl$cables <- 2 * observer_trawl$w_c * observer_trawl$c_c # Width of both cables (meters)
observer_trawl$sweep <- observer_trawl$w_s * observer_trawl$c_s # Width of the sweep (meters)
observer_trawl$lin_eff_width <- observer_trawl$boards + observer_trawl$cables + observer_trawl$sweep
observer_trawl$swept_area <- observer_trawl$d_t * (0.001 * observer_trawl$lin_eff_width) # SA without sensitivity (km)

```



## Categorizing Trawl Types 
```{r}
observer_trawl <- observer_trawl %>%
  mutate(NETTYPE = as.numeric(NETTYPE)) %>% 
  mutate(NETTYPE = replace_na(NETTYPE, 00)) %>%
  filter(!NETTYPE %in% c(76, 77, 75, 74, 78, 73, 61, 62, 60, 26, 27, 25)) %>%
      #filtering out net types that don't belong (pelagic, scallop, shrimp trawls)
      #76 - 2-seam pelagic pair trawl
      #77 - 4-seam pelagic pair trawl
      #75 - pelagic pair trawl, seams unknown
      #74 - 2-seam pelagic single trawl
      #78 - 4-seam pelagic single trawl
      #73 - pelagic single trawl, seams unknown
      #61 - 2-seam scallop trawl
      #62 - 4-seam scallop trawl
      #60 - scallop trawl, seams unknown
      #26 - 2-seam shrimp trawl 
      #27 - 4-seam shrimp trawl
      #25 - shrimp trawl, seams unknown
  mutate(trawl_type = case_when(
    NETTYPE %in% c(89, 90, 88, 24, 86, 87, 85) ~ 1, #Generic Groundfish Trawls 
      #89 - 2-seam balloon trawl 
      #90 - 4-seam balloon trawl 
      #88 - balloon trawl, seams unknown
      #24 - 4-seam box trawl
      #86 - 2-seam groundfish trawl 
      #87 - 4-seam groundfish trawl 
      #85 - groundfish trawl, seams unknown 
    NETTYPE %in% c(10, 11, 12, 13, 1, 2, 08, 66, 67, 65) ~ 2, #Flatfish Trawls
      #10 - flatfish trawl, seams unknown 
      #11 - 2-seam flatfish trawl 
      #12 - 4-seam flatfish trawl 
      #13 - flounder trawl 
      #01 - 2-seam flynet trawl
      #02 - 4-seam flynet trawl 
      #08 - flynet, seams unknown
      #66 - 2-seam monkfish trawl
      #67 - 4-seam monkfish trawl
      #65 - monkfish trawl, seams unknown 
    NETTYPE %in% c(3, 4, 9, 16, 6, 7, 5) ~ 3, #Separator Trawls
      #03 - 2-seam haddock separator trawl 
      #04 - 4-seam haddock separator trawl 
      #09 - haddock separator trawl, seams unknown 
      #16 - rope separator trawl 
      #06 - 2-seam separator trawl
      #07 - 4-seam separator trawl
      #05 - separator trawl, seams unknown 
    NETTYPE %in% c(31, 30, 32, 17, 18, 15, 81, 82, 80) ~ 4, #Eliminator Trawls
      #31 - 2-seam eliminator trawl
      #30 - 4-seam eliminator trawl
      #32 - eliminator trawl, seams unknown
      #17 - 4-seam mid-sized ruhle trawl
      #18 - 4-seam millionaire trawl
      #15 - 4-seam ruhle trawl
      #81 - 2-seam shuman trawl
      #82 - 4-seam shuman trawl
      #80 - shuman trawl, seams unknown
    NETTYPE %in% c(91, 92, 00, 99) ~ 5, #Other/Unknown Trawls

  ))

```

## Calculating catch per swept area
```{r}

#calculates the catch per swept area with just kept catch
sf_trawl <- sf_trawl %>% 
  group_by(EFFORT_ID, COMMON_NAME) %>%
  filter(DISPOSITION_CODE == "011") %>%
  mutate(sf_species_catch = sum(HAIL_AMOUNT_LB)) %>%
  ungroup() %>%
  mutate(sf_species_cpua = sf_species_catch/swept_area)


#calculates the catch per swept area for the observer data with just kept catch 
observer_trawl <- observer_trawl %>%
  filter(FISHDISP == 100) %>%
  group_by(trip_haul_ID, COMNAME) %>%
  mutate(ob_species_catch = sum(LIVE_WT)) %>%
  ungroup() %>%
  mutate(ob_species_cpua = ob_species_catch/swept_area)


#calculates the catch per swept area for the nefsc bottom trawl survey 
nefsc <- nefsc %>%
  rename(SWEPT_AREA = AREA_SWEPT_DOORS_MEAN_KM2) %>% 
  mutate(nefsc_species_cpua = CATCHWT_updated/SWEPT_AREA)

```


## Slimming datasets
```{r}
#selecting just the variables of interest for study fleet dataset 
sf_trawl_slim <- sf_trawl %>%
  select(c("TRIP_ID", "VESSEL_NAME", "TARGET_SPECIES", "trawl_type", 
           "EFFORT_ID", "COMMON_NAME", "NESPP4", "SPECIES_ITIS",
           "DISPOSITION_DESCR", "AREA_CODE", "SOAK_DUR_HRS", "EFFORT_NUM",
           "START_TOW_DATE_GMT", "END_TOW_DATE_GMT", "START_TOW_LAT",
           "START_TOW_LON", "END_TOW_LAT", "END_TOW_LON", "DEPTH_FTH", 
           "GEAR_QUANTITY", "GEAR_SIZE", "MESH_SIZE", "MESH_TYPE", 
           "HAIL_AMOUNT", "HAIL_AMOUNT_LB", "haul_dur_hr", "haul_dist_nm", 
           "MEAN_DPTH_M", "survey_comercial_ID", "strata", "swept_area",
           "sf_species_catch", "sf_species_cpua"))
  # select(-c("VES_NAME", "HULL_ID", "PPORT", "HPORT", "ACCSP_GEAR_CODE", 
  #           "PPST", "SAIL_PORT_NAME", "SAIL_STATE_POSTAL", "LAND_PORT_NAME", 
  #           "LAND_STATE_POSTAL", "START_SET_DATE_GMT", "START_SET_LAT", "START_SET_LON", 
  #           "END_HAUL_DATE_GMT")) %>%

  


#selecting just the variables of interest for observer dataset 
ob_trawl_slim <- observer_trawl %>%
  mutate(START_TOW_DATE = make_date(YEARHBEG, MONTHHBEG, DAYHBEG)) %>%
  select(c("trip_haul_ID", "START_TOW_DATE", "AREA", "VESSELNAME",  "NEGEAR", 
           "GEARNM", "NETNAME", "NETTYPE", "HDROPLEN", "FTROPLEN", "GRCABLEN", 
           "BRDTPLEN", "CODHUNG", "LINERHUNG", "EXCLUSD", "EXCLTYP", "NETOHORIZ", 
           "DOORSPREAD", "GRCABTYP", "BRDLGTYP", "FTROPTYP", "NSWEEPS", 
           "SWEEPDIA", "CODLINERUSD", "LINERMSIZE", "CODMSIZE", "MSWGTAVG", "NESPP4", 
           "COMNAME", "CATDISP", "FISHDISP", "FISHDISPDESC", "START_TOW_LAT", 
           "START_TOW_LON", "END_TOW_LAT", "END_TOW_LON", "HAULDUR", "HAILWT", 
           "LIVE_WT", "survey_comercial_ID", "strata", "trawl_type", "swept_area", 
           "ob_species_catch", "ob_species_cpua"))
         # "swept_area"))




#selecting just the variables of interest for the nefsc dataset 
nefsc_slim <- nefsc %>%
  select(c("cruise_station_ID", "STRATUM", "AREA", "SVVESSEL", "SVGEAR", 
           "START_TOW_DATE_GMT", "END_TOW_DATE_GMT", "START_TOW_LAT", 
           "START_TOW_LON", "END_TOW_LAT", "END_TOW_LON", 
           "TOWDUR", "AVGDEPTH", "AVGDEPTH", "AIRTEMP", "BAROPRESS", "WINDDIR", 
           "WINDSP", "WEATHER", "WAVEHGT", "SWELLDIR", "SWELLHGT", "SURFTEMP", 
           "SURFSALIN", "BOTTEMP", "BOTSALIN", "LOGGED_SPECIES_NAME", "SVSPP", 
           "EXPCATCHNUM", "EXPCATCHWT", "undersized_fish_WT", "CATCHWT_updated", 
           "SWEPT_AREA", "nefsc_species_cpua"))
  # select(-c("EST_MONTH","EST_DAY", "EST_JULIAN_DAY", "BEGLAT", "BEGLON", "ENDLAT", 
  #           "ENDLON", "COURSE", "RPM", "DOPDISTW", "...11", "...12", 
  #           "BEGIN_EST_TOWDATE", "END_EST_TOWDATE", "SURFSALIN", "SURFTEMP", 
  #           "XBT", "BKTTEMP", "SWELLHGT", "SWELLDIR", "WAVEHGT", "WEATHER", 
  #           "WINDSP", "WINDDIR", "BAROPRESS", "CLOUD", "AIRTEMP", "DESSPEED", "DOPDISTB", 
  #           "HEADING", "PITCH")) %>%

  


#selecting just the variables of interest for the VW dataset 
# vw_slim <- vw %>% 
#   select("TowID", "VesselID", "GearID", "START_TOW_DATE_GMT", "TowStartLat", 
#          "TowStartLong", "TowStartDepth", "END_TOW_DATE_GMT", "TowEndLat", 
#          "TowEndLong", "TowEndLong", "TowEndDepth", "SpeciesID", 
#          "common_name", "TotalWeight_lb") 

  

  

#creating a dataset for just the station info
# nefsc_station <- rbind(nefsc_station_fall, nefsc_station_spring)
# nefsc_station <- nefsc_station %>%
#   mutate(cruise_station_ID = paste(CRUISE6,STATION, sep = '_')) %>%
#   relocate(cruise_station_ID) %>%
#   filter(EST_YEAR >= 2009) %>%
#   mutate(BEGIN_EST_TOWDATE = as.POSIXct(BEGIN_EST_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
#   mutate(END_EST_TOWDATE = as.POSIXct(END_EST_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
#   mutate(BEGIN_GMT_TOWDATE = as.POSIXct(BEGIN_GMT_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
#   mutate(END_GMT_TOWDATE = as.POSIXct(END_GMT_TOWDATE, format = "%m/%d/%y %H:%M")) %>%
#   mutate(survey_commerical_ID = 1) %>%
# 
#   select(c("cruise_station_ID", "STRATUM", "AREA", "SVGEAR", 
#            "BEGIN_GMT_TOWDATE", "END_GMT_TOWDATE", "DECDEG_BEGLAT", 
#            "DECDEG_BEGLON", "DECDEG_ENDLAT", "DECDEG_ENDLON", 
#            "TOWDUR", "AVGDEPTH")) %>%
#   rename(START_TOW_DATE_GMT = BEGIN_GMT_TOWDATE) %>%
#   rename(END_TOW_DATE_GMT = END_GMT_TOWDATE) %>%
#   rename(START_TOW_LAT = DECDEG_BEGLAT) %>%
#   rename(START_TOW_LON = DECDEG_BEGLON) %>%
#   rename(END_TOW_LAT = DECDEG_ENDLAT) %>%
#   rename(END_TOW_LON = DECDEG_ENDLON) %>%
#   drop_na(END_TOW_LAT) %>%
#   drop_na(END_TOW_LON)

rm(sf_trawl)
rm(observer_trawl)
rm(nefsc)
# rm(vw)
```



# Renaming Variables of Interest (so they are consistent across datasets)
```{r}

```



# Saving the Slimmed Down Datasets 
```{r}
write.csv(sf_trawl_slim, './data/sf_trawl_slim.csv', row.names = FALSE)
write.csv(ob_trawl_slim, './data/ob_trawl_slim.csv', row.names = FALSE)
write.csv(nefsc_slim, './data/nefsc_slim.csv', row.names = FALSE)
# write.csv(vw_slim, './data/vw_slim.csv', row.names = FALSE)
```



