---
title: "relative_efficiency_analysis"
output: html_document
date: "2022-08-17"
---


```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(skimr)
library(data.table)
library(fuzzyjoin)
library(lubridate)
library(kableExtra)
library(modEvA)
library(GGally)

library(maps) # land masses
library(rgdal) # read OGR vector maps into Spatial objects
library(viridis) # for customizing scale bars
library(mapproj)
library(hexbin)
library(sf)
library(scales)
library(gridExtra)
library(openxlsx)
library(beepr)
library(purrr)
library(rsq)
```

# Read- In the Data
```{r}
paired_tows_1mi_24hr <- read.csv('./data/paired_tows_1mi_24hr.csv')
paired_tows_5mi_72hr <- read.csv('./data/paired_tows_5mi_72hr.csv')
```



# Data for Maps 
```{r}
#Additional Data for Maps
#Statistical Areas
sareas <- st_read(dsn = "./data/Statistical_Areas_2010_withNames") %>%
  st_set_crs(4269)
sareas <- sareas %>% filter(Id %in% c("464", "465", "511", "512", "513", "514", "515", "521", "522", "525", "526", "537", "538", "539", "551", "561", "562", "611", "612", "613", "543", "542", "541", "534", "533", "616", "615", "614", "621", "622", "623", "624"))  
centroids <- sf::st_coordinates(st_centroid(sareas)) 
areas <- cbind(sareas, centroids)


#Land Mass
states <- map_data("state")
NEUS <- subset(states, region %in% c("Maine", "massachusetts", "new hampshire", "vermont", "maine", "rhode island",
                "connecticut","new york","new jersey","delaware","pennsylvania",
                            "maryland","virginia","north carolina","west virginia"))


#NEFSC Survey Strata
sf::sf_use_s2(FALSE)
nefsc_strata <- st_read(dsn = "./data/strata") %>%
  st_set_crs(4269)


```



# Study Fleet and NEFSC Pairs
## 1m and 24hr Paired Tows 
### Comparing CPUA and Relative Efficiency 
```{r}
#filtering for just the species of interest and creating a relative efficiency variable and creating variables for modeling 
paired_tows_1mi_24hr_re <- paired_tows_1mi_24hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712 | #cod 
         SVSPP == 74 & SPECIES_ITIS == 164744 | #haddock
         SVSPP == 75 & SPECIES_ITIS == 164727 | #pollock
         SVSPP == 105 & SPECIES_ITIS == 172909 | #yellowtail flounder
         SVSPP == 102 & SPECIES_ITIS == 172877 | #american plaice
         SVSPP == 107 & SPECIES_ITIS == 172873 | #witch flounder
         SVSPP == 76 & SPECIES_ITIS == 164732  | #white hake
         SVSPP == 108 & SPECIES_ITIS == 172746 | #windowpane
         SVSPP == 106 & SPECIES_ITIS == 172905 | #winter flounder
         SVSPP == 155 & SPECIES_ITIS == 166774 | #acadian redfish
         SVSPP == 101 & SPECIES_ITIS == 172933 | #atlantic halibut   #NE Groundfish spp

    
         SVSPP == 72 & SPECIES_ITIS == 164791 | #silver hake
         SVSPP == 77 & SPECIES_ITIS == 164730 | #red hake
         SVSPP == 78 & SPECIES_ITIS == 164731 | #spotted hake
           
         SVSPP == 103 & SPECIES_ITIS == 172735 | #summer flounder
         SVSPP == 104 & SPECIES_ITIS == 172739 | #fourspot flounder
    
         SVSPP == 197 & SPECIES_ITIS == 164499 | #goosefish
         SVSPP == 15 & SPECIES_ITIS == 160617    #spiny dogfish
        ) %>%
  drop_na(sf_species_cpua, nefsc_species_cpua) %>%
  filter(CATCHWT_updated > 0) %>%
  mutate(old_relative_efficiency = log(sf_species_cpua)/log(nefsc_species_cpua)) %>%
  mutate(relative_efficiency = nefsc_species_cpua/(nefsc_species_cpua + sf_species_cpua)) %>%  
  mutate(mgmt_area = case_when(
    AREA_CODE %in% c(511, 512, 513, 514, 515) ~ "GOM", 
    AREA_CODE %in% c(521, 522, 526, 525, 561, 562, 551, 552) ~ "GB", 
    AREA_CODE %in% c(611, 612, 613, 539, 538, 537) ~ "SNE"
  )) %>%
  mutate(season = case_when(
    month(START_TOW_DATE_GMT.x) %in% c(03, 04, 05) ~ "Spring", 
    month(START_TOW_DATE_GMT.x) %in% c(09, 10, 11) ~ "Fall", 
  )) %>%
  distinct()
  # filter(SVSPP == 73)
  




#COD
#Looking at the cpua for the paired tows
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Atlantic Cod", 
       subtitle = "Pairs within 1 mi and 24 hrs")

#Looking at the relative efficiency of the study fleet catch to the science center survey 
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Atlantic Cod", 
       subtitle = "Pairs within 1 mi and 24 hrs")




#HADDOCK
#Looking at the cpua for the paired tows
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Haddock", 
       subtitle = "Pairs within 1 mi and 24 hrs")

#Looking at the relative efficiency of the study fleet catch to the science center survey 
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Haddock", 
       subtitle = "Pairs within 1 mi and 24 hrs")




#YELLOWTAIL FLOUNDER
#Looking at the cpua for the paired tows
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Yellowtail Flounder", 
       subtitle = "Pairs within 1 mi and 24 hrs")

#Looking at the relative efficiency of the study fleet catch to the science center survey 
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Yellowtail Flounder", 
       subtitle = "Pairs within 1 mi and 24 hrs")




#WINTER FLOUNDER
#Looking at the cpua for the paired tows
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Winter Flounder", 
       subtitle = "Pairs within 1 mi and 24 hrs")

#Looking at the relative efficiency of the study fleet catch to the science center survey 
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Winter Flounder", 
       subtitle = "Pairs within 1 mi and 24 hrs")




#MONKFISH
#Looking at the cpua for the paired tows
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Monkfish", 
       subtitle = "Pairs within 1 mi and 24 hrs")

#Looking at the relative efficiency of the study fleet catch to the science center survey 
paired_tows_1mi_24hr_re %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Monkfish", 
       subtitle = "Pairs within 1 mi and 24 hrs")


```


### Maps of Matched Tows 
```{r}
#plotting the matches for 1 mile and 24 hrs w Stat Areas
paired_tows_1mi_24hr_re %>%
  ggplot() + 
  geom_sf(data = areas, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = paired_tows_1mi_24hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = paired_tows_1mi_24hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 1 mi and 24 hrs")
```




## 5m and 72hr Paired Tows
### Comparing CPUA and Relative Efficiency 
```{r}
#filtering for just the species of interest and creating a relative efficiency variable and creating variables for modeling 
paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712 | #cod 
         SVSPP == 74 & SPECIES_ITIS == 164744 | #haddock
         SVSPP == 75 & SPECIES_ITIS == 164727 | #pollock
         SVSPP == 105 & SPECIES_ITIS == 172909 | #yellowtail flounder
         SVSPP == 102 & SPECIES_ITIS == 172877 | #american plaice
         SVSPP == 107 & SPECIES_ITIS == 172873 | #witch flounder
         SVSPP == 76 & SPECIES_ITIS == 164732  | #white hake
         SVSPP == 108 & SPECIES_ITIS == 172746 | #windowpane
         SVSPP == 106 & SPECIES_ITIS == 172905 | #winter flounder
         SVSPP == 155 & SPECIES_ITIS == 166774 | #acadian redfish
         SVSPP == 101 & SPECIES_ITIS == 172933 | #atlantic halibut   #NE Groundfish spp

    
         SVSPP == 72 & SPECIES_ITIS == 164791 | #silver hake
         SVSPP == 77 & SPECIES_ITIS == 164730 | #red hake
         SVSPP == 78 & SPECIES_ITIS == 164731 | #spotted hake
           
         SVSPP == 103 & SPECIES_ITIS == 172735 | #summer flounder
         SVSPP == 104 & SPECIES_ITIS == 172739 | #fourspot flounder
    
         SVSPP == 197 & SPECIES_ITIS == 164499 | #goosefish
         SVSPP == 15 & SPECIES_ITIS == 160617    #spiny dogfish
        ) %>%
  drop_na(sf_species_cpua, nefsc_species_cpua) %>%
  filter(CATCHWT_updated > 0) %>%
  filter(sf_species_cpua > 0) %>%
  mutate(old_relative_efficiency = log(sf_species_cpua)/log(nefsc_species_cpua)) %>%
  mutate(relative_efficiency = nefsc_species_cpua/(nefsc_species_cpua + sf_species_cpua)) %>%
  mutate(mgmt_area = case_when(
    AREA_CODE %in% c(511, 512, 513, 514, 515) ~ "GOM", 
    AREA_CODE %in% c(521, 522, 526, 525, 561, 562, 551, 552) ~ "GB", 
    AREA_CODE %in% c(611, 612, 613, 539, 538, 537) ~ "SNE"
  )) %>%
  mutate(season = case_when(
    month(START_TOW_DATE_GMT.x) %in% c(03, 04, 05) ~ "Spring", 
    month(START_TOW_DATE_GMT.x) %in% c(09, 10, 11) ~ "Fall", 
  )) %>%
  distinct() 




#COD
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#HADDOCK
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Haddock", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Haddock", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#WITCH FLOUNDER 
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 107 & SPECIES_ITIS == 172873) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Witch Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 107 & SPECIES_ITIS == 172873) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Witch Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#YELLOWTAIL FLOUNDER
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Yellowtail Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Yellowtail Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#AMERICAN PLAICE
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 102 & SPECIES_ITIS == 172877) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for American Plaice", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 102 & SPECIES_ITIS == 172877) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for American Plaice", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#WINTER FLOUNDER
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Winter Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Winter Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#MONKFISH
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Monkfish", 
       subtitle = "Pairs within 5 mi and 72 hrs") 

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  filter(sf_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 50, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Monkfish", 
       subtitle = "Pairs within 5 mi and 72 hrs")

  
```


### Maps of Matched Tows 
```{r}
#plotting the matches for 5 mi and 3 days 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = areas, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the GOM and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = areas, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(41.9, 43.3),  xlim = c(-71, -69.6)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the GB and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = areas, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(40.5, 42.5),  xlim = c(-69.6, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the SNE and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = areas, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(39.5, 41.5),  xlim = c(-72.2, -70.2)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")





################################################################################
#Same plots but with nefsc survey strata instead of stat atea 

paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the GOM and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(41.9, 43.3),  xlim = c(-71, -69.6)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the GB and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(40.5, 42.5),  xlim = c(-69.6, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")



#Zooming in on the SNE and looking at tow length for 5mi and 3 day matches 
paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  # geom_point(data = paired_tows_5mi_72hr, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
                                                y = START_TOW_LAT.x, yend = END_TOW_LAT.x, color = "NEFSC")) +
  geom_segment(data = paired_tows_5mi_72hr, aes(x = START_TOW_LON.y, xend = END_TOW_LON.y,
                                                y = START_TOW_LAT.y, yend = END_TOW_LAT.y, color = "Study Fleet")) +
  coord_sf(ylim = c(39.5, 41.5),  xlim = c(-72.2, -70.2)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue"))
# labs(title = "Study Fleet tows Matched to NEFSC tows", subtitle = "within 5 mi and 72 hrs")
```



# Statistical Analysis  
## Species Datasets
```{r}
#creating a separate dataset for each species 
#COD
cod_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#HADDOCK
haddock_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#WITCH FLOUNDER
witchfl_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 107 & SPECIES_ITIS == 172873) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#YELLLOWTAIL FLOUNDER
yellowtailfl_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#AMERICAN PLAICE
plaice_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 102 & SPECIES_ITIS == 172877) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#WINTER FLOUNDER
winterfl_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

#MONKFISH
monkfish_paired_tows_5mi_72hr_re <- paired_tows_5mi_72hr_re %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>% 
  distinct(EFFORT_ID, .keep_all = TRUE)

```


## Exploring Collinearrity Among Explanatory Variables 
```{r}
ggpairs(cod_paired_tows_5mi_72hr_re, 
        columns = c("relative_efficiency", "season", "mgmt_area", "VESSEL_NAME", "AVGDEPTH", "BOTTEMP"), 
        cardinality_threshold = 17)

paired_tows_5mi_72hr_re %>%
  filter(nefsc_species_cpua < 50000, 
         sf_species_cpua < 50000) %>%
  ggplot() + 
  geom_point(aes(x = nefsc_species_cpua, y = sf_species_cpua))


```


## Function Creation 
```{r}
#################### FUNCTIONS FOR T-TESTS ####################################
#boxplot for the difference in CPUA
box.plot_diff <- function(x) {
  x %>% 
  ggplot() + 
  geom_boxplot(aes(y = diff)) + 
  labs(y = bquote("Difference between Study Fleet and NEFSC CPUA [lb/"*km^2*"]")) + 
  theme_classic()
}

#boxplot for the difference of the log(CPUA)
box.plot_diff_log <- function(x) {
  x %>% 
  ggplot() + 
  geom_boxplot(aes(y = diff_of_logs)) + 
  labs(y = bquote("Ln(Difference between Study Fleet and NEFSC CPUA [lb/"*km^2*"])")) + 
  theme_classic()
}

#histogram of the difference in CPUA
hist_kh_diff <- function(x) {
  x %>%  
  ggplot() + 
  geom_histogram(aes(x = diff)) + 
  labs(x = bquote("Difference between Study Fleet and NEFSC CPUA [lb/"*km^2*"]"), 
       y = "Count") + 
  theme_classic()
}

#histogram of the difference in log(CPUA)
hist_kh_diff_log <- function(x) {
  x %>%  
  ggplot() + 
  geom_histogram(aes(x = diff_of_logs)) + 
  labs(x = bquote("Ln(Difference between Study Fleet and NEFSC CPUA [lb/"*km^2*"])"), 
       y = "Count") + 
  theme_classic()
}


####################### STUFF I DIDNT END UP USING ############################

CPUA_label <- bquote("CPUA [lb/"*km^2*"]")
logCPUA_lable <- bquote("Log(CPUA [lb/"*km^2*"])")

#plots to check for normality before t-tests 
#boxplot of catch per unit area
box.plot <- function(x) {
  x %>%
  pivot_longer(cols = c(sf_species_cpua, nefsc_species_cpua),
               names_to = "Trawl",
               values_to = "CPUA") %>%
  filter(CPUA < 10000) %>%
  ggplot() +
  geom_boxplot(aes(x = Trawl, y = CPUA)) +
  labs(x = "Trawl Type", y = CPUA_label) +
  scale_x_discrete(labels = c("nefsc_species_cpua" = "NEFSC",
                              "sf_species_cpua" = "Study Fleet")) +
  theme_classic()
}

#histogram of catch per unit area
hist_kh <- function(x) {
  x %>%
  ggplot() +
  geom_histogram(aes(x = sf_species_cpua, y = ..density.., fill = "Study Fleet")) +
  # geom_label(aes(x = Inf, y = Inf, label = "Study Fleet CPUE", vjust =1 , hjust = 1), color = "red") +
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density.., fill = "NEFSC")) +
  # geom_label(aes(x = Inf, y = -Inf, label = "NEFSC CPUE", vjust = -1, hjust = 1), color = "blue") +
  labs(x = CPUA_label, y = "Density",
       # title = "Histogram of CPUE for x",
       # subtitle = "Pairs within 5 mi and 72 hrs"
       ) +
  xlim(0,2000) +
  scale_fill_manual(name = "Dataset",
                    values = c("Study Fleet" = "red", "NEFSC" = "blue"),
                    labels = c("Study Fleet", "NEFSC")) +
  theme_classic()
}

  
 
# #boxplot with log-transformed data 
# box.log.plot <- function(x) {
#   x %>% 
#   pivot_longer(cols = c(log_sf_species_cpua, log_nefsc_species_cpua), 
#                names_to = "Trawl", 
#                values_to = "CPUA") %>%
#   filter(CPUA < 10000) %>%
#   ggplot() + 
#   geom_boxplot(aes(x = Trawl, y = CPUA)) + 
#   labs(x = "Trawl Type", y = logCPUA_lable) + 
#   scale_x_discrete(labels = c("log_nefsc_species_cpua" = "NEFSC", 
#                               "log_sf_species_cpua" = "Study Fleet")) + 
#   theme_classic()
# }
# 
# #histogram with log-transformed data 
# hist_log_kh <- function(x) {
#   x %>%  
#   ggplot() + 
#   geom_histogram(aes(x = log_sf_species_cpua, y = ..density.., fill = "Study Fleet")) + 
#   # geom_label(aes(x = Inf, y = Inf, label = "Study Fleet CPUE", vjust =1 , hjust = 1), color = "red") +
#   geom_histogram(aes(x = log_nefsc_species_cpua, y = -..density.., fill = "NEFSC")) + 
#   # geom_label(aes(x = Inf, y = -Inf, label = "NEFSC CPUE", vjust = -1, hjust = 1), color = "blue") +
#   labs(x = logCPUA_lable, y = "Density", 
#        # title = "Histogram of CPUE for x", 
#        # subtitle = "Pairs within 5 mi and 72 hrs"
#        ) + 
#   scale_fill_manual(name = "Dataset", 
#                     values = c("Study Fleet" = "red", "NEFSC" = "blue"), 
#                     labels = c("Study Fleet", "NEFSC")) + 
#   theme_classic()
# }
# 



######################## FUNCTIONS FOR MODELLING #############################

#trying to  create functions because I will be running the same models for every species dataset 
covars <- c("season", "mgmt_area", "AVGDEPTH", "BOTTEMP")
combos <- purrr::map(1:4, ~as.data.frame(t(combn(covars, .x))))

formulae <- combos %>%
  map_dfr(unite, col="formula", sep = " + ") %>%
  mutate(formula = paste0("relative_efficiency ~  VESSEL_NAME +", formula))


#fit models (takes dataset)
fit.models <- function(x) {
  formulae$formula %>% purrr::map( ~glm(.x, family = binomial, data=x))
}


#compare models (takes list of models created by fit.models())
compare.models <- function(x) {
  formulae %>%
  mutate(aic =  purrr::map_dbl(x, AIC)) %>%
  arrange(desc(aic)) %>%
  mutate(deltaAIC = aic - aic[15]) %>%
  mutate(rsq =  purrr::map_dbl(x, Dsquared)) %>% 
  mutate(rsq = sprintf("%0.2f", rsq)) %>%
  mutate(aic = sprintf("%1.0f", aic)) %>%
  mutate(deltaAIC = sprintf("%1.0f", deltaAIC)) %>%
  kbl(col.names = (c("Model", "AIC", "deltaAIC","Deviance Explained"))) %>%
  kable_classic("striped", full_width = FALSE)
}


```



# Statistical Analysis by Species 
## Cod 
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(cod_paired_tows_5mi_72hr_re)
hist_kh(cod_paired_tows_5mi_72hr_re)

#log-transforming the data
cod_paired_tows_5mi_72hr_re <- cod_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(cod_paired_tows_5mi_72hr_re)
hist_kh_diff(cod_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(cod_paired_tows_5mi_72hr_re)
hist_kh_diff_log(cod_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data


#running t-test
cod_ttest <- t.test(cod_paired_tows_5mi_72hr_re$log_sf_species_cpua, cod_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
cod_ttest


#back transform the estimate
exp(cod_ttest$estimate)
exp(cod_ttest$conf.int)

```


#### Model Runs
```{r}
#COD
codm <- fit.models(cod_paired_tows_5mi_72hr_re)

compare.models(codm)

#storing the optimal model and plotting the diagnostics
codm_optimal <- glm(relative_efficiency ~ VESSEL_NAME +season + BOTTEMP, family = binomial, data = cod_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(codm_optimal)

```


## Haddock
#### T-test 
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(haddock_paired_tows_5mi_72hr_re)
hist_kh(haddock_paired_tows_5mi_72hr_re)

#log-transforming the data
haddock_paired_tows_5mi_72hr_re <- haddock_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(haddock_paired_tows_5mi_72hr_re)
hist_kh_diff(haddock_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(haddock_paired_tows_5mi_72hr_re)
hist_kh_diff_log(haddock_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are reasonably met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

#NOT SURE IF THIS SHOULD BE DONE WITH A WELCH T-TEST????

haddock_ttest <- t.test(haddock_paired_tows_5mi_72hr_re$log_sf_species_cpua, haddock_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
haddock_ttest

#back transform the estimate
exp(haddock_ttest$estimate)
exp(haddock_ttest$conf.int)

```


#### Model Runs 
```{r}
#HADDOCK
haddockm <- fit.models(haddock_paired_tows_5mi_72hr_re)

compare.models(haddockm)


#storing the optimal model and plotting the diagnostics
haddockm_optimal <- glm(relative_efficiency ~ VESSEL_NAME + season + BOTTEMP, family = binomial, data = haddock_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(haddockm_optimal)

```



## Witch Flounder
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(witchfl_paired_tows_5mi_72hr_re)
hist_kh(witchfl_paired_tows_5mi_72hr_re)

#log-transforming the data
witchfl_paired_tows_5mi_72hr_re <- witchfl_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(witchfl_paired_tows_5mi_72hr_re)
hist_kh_diff(witchfl_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(witchfl_paired_tows_5mi_72hr_re)
hist_kh_diff_log(witchfl_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are not met with the log transformed data, 
#so the non-parametric t-test alternative was conducted

#NOT SURE IF THIS SHOULD BE DONE WITH A WELCH T-TEST????


witchfl_ttest <- t.test(witchfl_paired_tows_5mi_72hr_re$log_sf_species_cpua, witchfl_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE, var.equal = FALSE)
witchfl_ttest

#back transform the estimate
exp(witchfl_ttest$estimate)
exp(witchfl_ttest$conf.int)

```


#### Model Runs
```{r}
#WITCH FLOUNDER 
witchflm <- fit.models(witchfl_paired_tows_5mi_72hr_re)

compare.models(witchflm)


#storing the optimal model and plotting the diagnostics
witchflm_optimal <- glm(relative_efficiency ~ VESSEL_NAME +BOTTEMP, family = binomial, data = witchfl_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(witchflm_optimal)
```


## Yewllowtail Flounder
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(yellowtailfl_paired_tows_5mi_72hr_re)
hist_kh(yellowtailfl_paired_tows_5mi_72hr_re)

#log-transforming the data
yellowtailfl_paired_tows_5mi_72hr_re <- yellowtailfl_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(yellowtailfl_paired_tows_5mi_72hr_re)
hist_kh_diff(yellowtailfl_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(yellowtailfl_paired_tows_5mi_72hr_re)
hist_kh_diff_log(yellowtailfl_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are not met with the log transformed data, 
#so the t-test was conducted with the log-transformed data


yellowtail_ttest <- t.test(yellowtailfl_paired_tows_5mi_72hr_re$log_sf_species_cpua, yellowtailfl_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
yellowtail_ttest

#back transform the estimate
exp(yellowtail_ttest$estimate)
exp(yellowtail_ttest$conf.int)

```


#### Model Runs
```{r}
#YELLOWTAIL FLOUNDER
yellowtailflm <- fit.models(yellowtailfl_paired_tows_5mi_72hr_re)

compare.models(yellowtailflm)


#storing the optimal model and plotting the diagnostics
yellowtailflm_optimal <- glm(relative_efficiency ~ VESSEL_NAME +AVGDEPTH + BOTTEMP, family = binomial, data = yellowtailfl_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(yellowtailflm_optimal)

```

## American Plaice
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(plaice_paired_tows_5mi_72hr_re)
hist_kh(plaice_paired_tows_5mi_72hr_re)

#log-transforming the data
plaice_paired_tows_5mi_72hr_re <- plaice_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(plaice_paired_tows_5mi_72hr_re)
hist_kh_diff(plaice_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(plaice_paired_tows_5mi_72hr_re)
hist_kh_diff_log(plaice_paired_tows_5mi_72hr_re)


#assumptions of normality and equal variance are not met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

plaice_ttest <- t.test(plaice_paired_tows_5mi_72hr_re$log_sf_species_cpua, plaice_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
plaice_ttest


#back transform the estimate
exp(plaice_ttest$estimate)
exp(plaice_ttest$conf.int)

```


#### Model Runs 
```{r}
#AMERICAN PLAICE 
plaicem <- fit.models(plaice_paired_tows_5mi_72hr_re)

compare.models(plaicem)


#storing the optimal model and plotting the diagnostics
plaicem_optimal <- glm(relative_efficiency ~ VESSEL_NAME +BOTTEMP, family = binomial, data = plaice_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(plaicem_optimal)

```


## Winter Flounder
####T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(winterfl_paired_tows_5mi_72hr_re)
hist_kh(winterfl_paired_tows_5mi_72hr_re)

#log-transforming the data
winterfl_paired_tows_5mi_72hr_re <- winterfl_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(winterfl_paired_tows_5mi_72hr_re)
hist_kh_diff(winterfl_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(winterfl_paired_tows_5mi_72hr_re)
hist_kh_diff_log(winterfl_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are not met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

winterfl_ttest <- t.test(winterfl_paired_tows_5mi_72hr_re$log_sf_species_cpua, winterfl_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
winterfl_ttest


#back transform the estimate
exp(winterfl_ttest$estimate)
exp(winterfl_ttest$conf.int)

```


#### Model Runs
```{r}
#WINTER FLOUNDER 
winterflm <- fit.models(winterfl_paired_tows_5mi_72hr_re)

compare.models(winterflm)


#storing the optimal model and plotting the diagnostics
winterflm_optimal <- glm(relative_efficiency ~ VESSEL_NAME +AVGDEPTH + BOTTEMP, family = binomial, data = winterfl_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(winterflm_optimal)

```


## Monkfish 
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(monkfish_paired_tows_5mi_72hr_re)
hist_kh(monkfish_paired_tows_5mi_72hr_re)

#log-transforming the data
monkfish_paired_tows_5mi_72hr_re <- monkfish_paired_tows_5mi_72hr_re %>%
  mutate(diff = sf_species_cpua - nefsc_species_cpua,
         log_sf_species_cpua = log(sf_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua), 
         diff_of_logs = log_sf_species_cpua - log_nefsc_species_cpua)

#looking at the boxplot and histograms of the difference between CPUA
box.plot_diff(monkfish_paired_tows_5mi_72hr_re)
hist_kh_diff(monkfish_paired_tows_5mi_72hr_re)

#looking at the boxplot and histograms of the diff_of_logs
box.plot_diff_log(monkfish_paired_tows_5mi_72hr_re)
hist_kh_diff_log(monkfish_paired_tows_5mi_72hr_re)

#assumptions of normality and equal variance are not met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

monkfish_ttest <- t.test(monkfish_paired_tows_5mi_72hr_re$log_sf_species_cpua, monkfish_paired_tows_5mi_72hr_re$log_nefsc_species_cpua, paired = TRUE)
monkfish_ttest


#back transform the estimate
exp(monkfish_ttest$estimate)
exp(monkfish_ttest$conf.int)

```



#### Model Run
```{r}
#MONKFISH 
monkfishm <- fit.models(monkfish_paired_tows_5mi_72hr_re)

compare.models(monkfishm)


#storing the optimal model and plotting the diagnostics
monkfishm_optimal <- glm(relative_efficiency ~ VESSEL_NAME +BOTTEMP, family = binomial, data = monkfish_paired_tows_5mi_72hr_re)

par(mfrow=c(2,2))
plot(monkfishm_optimal)

```

# Plotting the Matches for each Species 
```{r}
#COD
cod_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = cod_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = cod_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Cod", subtitle = "within 5 mi and 72 hrs")



#HADDOCK
haddock_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = haddock_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = haddock_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Haddock", subtitle = "within 5 mi and 72 hrs")




#WITCH FLOUNDER 
witchfl_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = witchfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = witchfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Witch Flounder", subtitle = "within 5 mi and 72 hrs")



#YELLOWTAIL FLOUNDER
yellowtailfl_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = yellowtailfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = yellowtailfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Yellowtail", subtitle = "within 5 mi and 72 hrs")



#AMERICAN PLAICE 
plaice_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = plaice_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = plaice_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Plaice", subtitle = "within 5 mi and 72 hrs")



#WINTER FLOUNDER 
winterfl_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = winterfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = winterfl_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Winter Flounder", subtitle = "within 5 mi and 72 hrs")



#MONKFISH
monkfish_paired_tows_5mi_72hr_re %>%
  ggplot() + 
  geom_sf(data = nefsc_strata, fill = "grey") +
  geom_polygon(data = NEUS, aes(x=long, y = lat, group = group), fill = "darkgreen",  
               color="black",inherit.aes = FALSE)  +
  geom_point(data = monkfish_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.x,y = END_TOW_LAT.x, color = "NEFSC")) +
  geom_point(data = monkfish_paired_tows_5mi_72hr_re, aes(x = END_TOW_LON.y,y = END_TOW_LAT.y, color = "Study Fleet")) +
  
  # geom_segment(data = paired_tows_1mi_24hr, aes(x = START_TOW_LON.x, xend = END_TOW_LON.x,
  #                                               y = START_TOW_LAT.x, yend = END_TOW_LAT.x)) +
  coord_sf(ylim = c(39, 44),  xlim = c(-74, -66)) + 
  scale_colour_manual("", breaks = c("NEFSC", "Study Fleet"), values = c("red", "blue")) +
  labs(title = "Study Fleet tows Matched to NEFSC tows - Monkfish", subtitle = "within 5 mi and 72 hrs")
```





# Trip ID for Study Fleet for Andy Jones 
```{r, eval = FALSE}
#Pulling out the study fleet trips to see if Andy Jones can talk to the captains 
#and figure out what kind of trawl net they were using 

#pulling out the unique effort ID and selecting the variables of interest 
SF_trips_1_24 <- paired_tows_1mi_24hr_logre %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  select(TRIP_ID, VESSEL_NAME, TARGET_SPECIES, VTR_GEAR_CODE, EFFORT_ID, AREA_CODE, 
         START_TOW_DATE_GMT.y, END_TOW_DATE_GMT.y, START_TOW_LAT.y, START_TOW_LON.y, 
         END_TOW_LAT.y, END_TOW_LON.y, DEPTH_FTH, GEAR_QUANTITY, GEAR_SIZE, MESH_SIZE) %>%
  rename(START_TOW_DATE_GMT = START_TOW_DATE_GMT.y, 
         END_TOW_DATE_GMT = END_TOW_DATE_GMT.y, 
         START_TOW_LAT = START_TOW_LAT.y, 
         START_TOW_LON = START_TOW_LON.y, 
         END_TOW_LAT = END_TOW_LAT.y, 
         END_TOW_LON = END_TOW_LON.y
         )

#doing the same thing for the 5mi and 72hr matches 
SF_trips_5_72 <- paired_tows_5mi_72hr_logre %>%
  distinct(EFFORT_ID, .keep_all = TRUE) %>%
  select(TRIP_ID, VESSEL_NAME, TARGET_SPECIES, VTR_GEAR_CODE, EFFORT_ID, AREA_CODE, 
         START_TOW_DATE_GMT.y, END_TOW_DATE_GMT.y, START_TOW_LAT.y, START_TOW_LON.y, 
         END_TOW_LAT.y, END_TOW_LON.y, DEPTH_FTH, GEAR_QUANTITY, GEAR_SIZE, MESH_SIZE) %>%
  rename(START_TOW_DATE_GMT = START_TOW_DATE_GMT.y, 
         END_TOW_DATE_GMT = END_TOW_DATE_GMT.y, 
         START_TOW_LAT = START_TOW_LAT.y, 
         START_TOW_LON = START_TOW_LON.y, 
         END_TOW_LAT = END_TOW_LAT.y, 
         END_TOW_LON = END_TOW_LON.y
         )



#Getting ready to export the study fleet trip data

#define sheets name for each dataframe
#only included species that had more than 5 observations 
dataset_names <- list("Trips_1mi_24hr" = SF_trips_1_24, 
                      "Trips_5mi_72hr" = SF_trips_5_72)

#export each data frame to separate sheets in same Excel file
openxlsx::write.xlsx(dataset_names, file = 'StudyFleet_Trips.xlsx', rowNames = FALSE)

```


# Trash 
```{r, include = FALSE, eval=FALSE}
##just me trying out different code 
#basically it's all trash 













p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 73) %>%
  ggplot() + 
  geom_histogram(aes(x = nefsc_species_cpua, fill = "blue", alpha=0.4, bins = 30)) + 
  geom_histogram(aes(x = sf_species_cpua, fill = "red", alpha=0.4, bins = 30)) + 
  xlim(0, 2000)






#looking at the differences in efficiency between the bigelow and the stuff fleet
#COD
g1 <- p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 73) %>%
  ggplot() + 
  geom_histogram(aes(x = nefsc_species_cpua, fill = "blue")) + 
  xlim(0,2000)
  
  
g2 <-  p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 73) %>%
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, fill = "red")) + 
  xlim(0,2000)

grid.arrange(g1, g2)


#HADDOCK 
g1 <- p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 74) %>%
  ggplot() + 
  geom_histogram(aes(x = nefsc_species_cpua, fill = "blue")) + 
  xlim(0,2000)
  
  
g2 <-  p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 74) %>%
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, fill = "red")) + 
  xlim(0,2000)

grid.arrange(g1, g2)



#YELLOWTAIL
g1 <- p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 74) %>%
  ggplot() + 
  geom_histogram(aes(x = nefsc_species_cpua, fill = "blue")) + 
  xlim(0,2000)
  
  
g2 <-  p2 %>%
  drop_na(nefsc_species_cpua, sf_species_cpua) %>%
  filter(SVSPP == 74) %>%
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, fill = "red")) + 
  xlim(0,2000)

grid.arrange(g1, g2)




#COD
paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% #cod
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, y = ..density..), fill = "red", bins = 100) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue", bins = 100) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb/min)", y = "Density", 
       title = "Histogram of CPUE for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  xlim(0,2000)

#COD but log(CPUA)
paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% #cod
  mutate(log_sf_species_cpua = log(sf_species_cpua)) %>%
  mutate(log_nefsc_species_cpua = log(nefsc_species_cpua)) %>%
  ggplot() + 
  geom_histogram(aes(x = log_sf_species_cpua, y = ..density..), fill = "red", bins = 100) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = log_nefsc_species_cpua, y = -..density..), fill = "blue", bins = 100) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb/min)", y = "Density", 
       title = "Histogram of ln(CPUE) for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs")






#HADDOCK
paired_tows_5mi_72hr %>%
  filter(SVSPP == 74 & SPECIES_ITIS == 164744) %>% #haddock
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, y = ..density..), fill = "red", bins = 50) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue", bins = 50) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb / km2)", y = "Density", 
       title = "Histogram of CPUE for Haddock", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  xlim(0,2000)


#YELLOWTAIL
paired_tows_5mi_72hr %>%
  filter(SVSPP == 105 & SPECIES_ITIS == 172909) %>% #yellowtail
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, y = ..density..), fill = "red", bins = 50) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue", bins = 50) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb / km2)", y = "Density", 
       title = "Histogram of CPUE for Yellowtail", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  xlim(0,2000)

#WINTER FLOUNDER
paired_tows_5mi_72hr %>%
  filter(SVSPP == 106 & SPECIES_ITIS == 172905) %>% #winter flounder
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, y = ..density..), fill = "red", bins = 100) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue", bins = 100) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb / km2)", y = "Density", 
       title = "Histogram of CPUE for Winter Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  xlim(0,2000)


#MONKFISH
paired_tows_5mi_72hr %>%
  filter(SVSPP == 197 & SPECIES_ITIS == 164499) %>% #monkfish
  ggplot() + 
  geom_histogram(aes(x = sf_species_cpua, y = ..density..), fill = "red", bins = 100) + 
  # geom_label(aes(x = 7, y = 0.4, label = "Study Fleet CPUE"), color = "red") + 
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue", bins = 100) + 
  # geom_label(aes(x = 7, y = -0.4, label = "NEFSC CPUE"), color = "blue") + 
  labs(x = "CPUA (lb/min)", y = "Density", 
       title = "Histogram of CPUE for Monkfish", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  xlim(0,2000)


#AMERICAN PLAICE






###############################################################################
paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% #cod
  ggplot(aes(y = log(sf_species_cpua))) + 
  geom_bar(stat = "identity", position = "identity")


paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  select(sf_species_cpua, )


paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  filter(sf_species_cpua < 2000) %>%
  filter(nefsc_species_cpua < 2000) %>%
  ggplot() + 
  geom_bar(aes(x = EFFORT_ID, y = sf_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = EFFORT_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue")



paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>% 
  drop_na(sf_species_cpua, nefsc_species_cpua) %>%
  mutate(relative_efficiency = log(sf_species_cpua)/log(nefsc_species_cpua)) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  xlim(0, 4) + 
  geom_vline(aes(xintercept=1),
            color="red", linetype="dashed", size=1)




paired_tows_5mi_72hr %>%
  filter(SVSPP == 73 & SPECIES_ITIS == 164712) %>%
  select(nefsc_species_cpua, sf_species_cpua) %>%
  pivot_longer(cols = c("nefsc_species_cpua", "sf_species_cpua"), 
               names_to = "trawl_type", 
               values_to = "cpua")

  






  count(sf_species_cpua)
  

  
  
```

