---
title: "relative_efficiency_analysis_observer"
output: html_document
date: "2022-10-05"
---



```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(skimr)
library(data.table)
library(fuzzyjoin)
library(lubridate)
library(kableExtra)
library(modEvA)

library(maps) # land masses
library(rgdal) # read OGR vector maps into Spatial objects
library(viridis) # for customizing scale bars
library(mapproj)
library(hexbin)
library(sf)
library(scales)
library(gridExtra)
library(openxlsx)
library(beepr)
library(purrr)
library(broom)
library(aod)
```

# Read-In the Data
```{r}
paired_tows_1mi_24hr_ob <- read.csv('./data/paired_tows_1mi_24hr_ob.csv')
paired_tows_5mi_72hr_ob <- read.csv('./data/paired_tows_5mi_72hr_ob.csv')
```


# Data for Maps 
```{r}
#Additional Data for Maps
#Statistical Areas
sareas <- st_read(dsn = "./data/Statistical_Areas_2010_withNames") %>%
  st_set_crs(4269)
sareas <- sareas %>% filter(Id %in% c("464", "465", "511", "512", "513", "514", "515", "521", "522", "525", "526", "537", "538", "539", "551", "561", "562", "611", "612", "613", "543", "542", "541", "534", "533", "616", "615", "614", "621", "622", "623", "624"))  
centroids <- sf::st_coordinates(st_centroid(sareas)) 
areas <- cbind(sareas, centroids)


#Land Mass
states <- map_data("state")
NEUS <- subset(states, region %in% c("Maine", "massachusetts", "new hampshire", "vermont", "maine", "rhode island",
                "connecticut","new york","new jersey","delaware","pennsylvania",
                            "maryland","virginia","north carolina","west virginia"))


#NEFSC Survey Strata
sf::sf_use_s2(FALSE)
nefsc_strata <- st_read(dsn = "./data/strata") %>%
  st_set_crs(4269)


```





# Observer and NEFSC Pairs
## 1m and 24hr Paired Tows 
### Comparing CPUA and Relative Efficiency 
```{r}
paired_tows_1mi_24hr_ob_logre <- paired_tows_1mi_24hr_ob %>%
  filter(SVSPP == 73 & NESPP4 == 818 | #cod 
         SVSPP == 74 & NESPP4 == 1477 | #haddock
         SVSPP == 75 & NESPP4 == 2695 | #pollock
         SVSPP == 105 & NESPP4 == 1230 | #yellowtail flounder
         SVSPP == 102 & NESPP4 == 1240 | #american plaice
         SVSPP == 107 & NESPP4 == 1220 | #witch flounder
         SVSPP == 108 & NESPP4 == 1250 | #windowpane
         SVSPP == 106 & NESPP4 == 1200 | #winter flounder
         SVSPP == 155 & NESPP4 == 2400 | #acadian redfish
         SVSPP == 197 & NESPP4 == 124    #monkfish
        ) %>%
  drop_na(ob_species_cpua, nefsc_species_cpua) %>%
  filter(CATCHWT_updated > 0) %>%
  mutate(relative_efficiency = log(ob_species_cpua)/log(nefsc_species_cpua)) %>%
  mutate(mgmt_area = case_when(
    AREA.x %in% c(511, 512, 513, 514, 515) ~ "GOM", 
    AREA.x %in% c(521, 522, 526, 525, 561, 562, 551, 552) ~ "GB", 
    AREA.x %in% c(611, 612, 613, 539, 538, 537) ~ "SNE"
  )) %>%
  mutate(season = case_when(
    month(START_TOW_DATE_GMT) %in% c(03, 04, 05) ~ "Spring", 
    month(START_TOW_DATE_GMT) %in% c(09, 10, 11) ~ "Fall", 
  )) %>%
  distinct()



```


## 5m and 72hr Paired Tows
### Comparing CPUA and Relative Efficiency 
```{r}
paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob %>%
  filter(SVSPP == 73 & NESPP4 == 818 | #cod 
         SVSPP == 74 & NESPP4 == 1477 | #haddock
         SVSPP == 75 & NESPP4 == 2695 | #pollock
         SVSPP == 105 & NESPP4 == 1230 | #yellowtail flounder
         SVSPP == 102 & NESPP4 == 1240 | #american plaice
         SVSPP == 107 & NESPP4 == 1220 | #witch flounder
         SVSPP == 108 & NESPP4 == 1250 | #windowpane
         SVSPP == 106 & NESPP4 == 1200 | #winter flounder
         SVSPP == 155 & NESPP4 == 2400 | #acadian redfish
         SVSPP == 197 & NESPP4 == 124    #monkfish
        ) %>%
  drop_na(ob_species_cpua, nefsc_species_cpua) %>%
  filter(CATCHWT_updated > 0) %>%
  mutate(old_relative_efficiency = log(ob_species_cpua)/log(nefsc_species_cpua)) %>%
  mutate(relative_efficiency = nefsc_species_cpua/(nefsc_species_cpua + ob_species_cpua)) %>%
  mutate(mgmt_area = case_when(
    AREA.x %in% c(511, 512, 513, 514, 515) ~ "GOM", 
    AREA.x %in% c(521, 522, 526, 525, 561, 562, 551, 552) ~ "GB", 
    AREA.x %in% c(611, 612, 613, 539, 538, 537) ~ "SNE"
  )) %>%
  mutate(season = case_when(
    month(START_TOW_DATE_GMT) %in% c(03, 04, 05) ~ "Spring", 
    month(START_TOW_DATE_GMT) %in% c(09, 10, 11) ~ "Fall", 
  )) %>%
  mutate(trawl_type = as.factor(trawl_type)) %>%
  distinct()






#COD
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 73 & NESPP4 == 818) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 73 & NESPP4 == 818) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Atlantic Cod", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#HADDOCK
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 74 & NESPP4 == 1477) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Haddock", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 74 & NESPP4 == 1477) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Haddock", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#WITCH FLOUNDER 
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 107 & NESPP4 == 1220) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Witch Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 107 & NESPP4 == 1220) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Witch Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#YELLOWTAIL FLOUNDER
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 105 & NESPP4 == 1230) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Yellowtail Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 105 & NESPP4 == 1230) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Yellowtail Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#AMERICAN PLAICE
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 102 & NESPP4 == 1240) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for American Plaice", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 102 & NESPP4 == 1240) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for American Plaice", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#WINTER FLOUNDER
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 106 & NESPP4 == 1200) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Winter Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 106 & NESPP4 == 1200) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Winter Flounder", 
       subtitle = "Pairs within 5 mi and 72 hrs")




#MONKFISH
#Looking at the cpua for the paired tows for each species 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 197 & NESPP4 == 124) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() + 
  geom_bar(aes(x = trip_haul_ID, y = ob_species_cpua), stat = "identity", fill = "red") + 
  geom_bar(aes(x = trip_haul_ID, y = -nefsc_species_cpua), stat = "identity", fill = "blue") + 
  labs(x = "Tow Number", y = "CPUA (lbs/km2)", 
       title = "Comparison of CPUA for Monkfish", 
       subtitle = "Pairs within 5 mi and 72 hrs") 

#Looking at the relative efficiency of the study fleet tows compared to the nefsc survey 
paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 197 & NESPP4 == 124) %>%
  distinct(trip_haul_ID, .keep_all = TRUE) %>%
  filter(ob_species_cpua < 10000) %>%
  filter(nefsc_species_cpua < 10000) %>%
  ggplot() +
  geom_histogram(aes(x = relative_efficiency), bins = 100, color = "black", fill = "white") + 
  geom_vline(aes(xintercept = 0.5),
            color = "black", linetype = "dashed", size = 1) + 
  geom_vline(aes(xintercept = mean(relative_efficiency)),
            color = "red", linetype = "dashed", size = 1) + 
  labs(x = "Relative Efficiency", y = "Count", 
       title = "Histogram of Relative Efficiency for Monkfish", 
       subtitle = "Pairs within 5 mi and 72 hrs")

  
```


### Maps of Matched Tows 
```{r}

```






# Statistical Analysis
## Species Datasets
```{r}
#creating a separate dataset for each species 
#COD
cod_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 73 & NESPP4 == 818) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE)

#HADDOCK
haddock_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 74 & NESPP4 == 1477) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE)

#WITCH FLOUNDER
witchfl_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 107 & NESPP4 == 1220) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE)

#YELLLOWTAIL FLOUNDER
yellowtailfl_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 105 & NESPP4 == 1230) %>% 
  distinct(trip_haul_ID, .keep_all = TRUE)

#AMERICAN PLAICE
plaice_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 102 & NESPP4 == 1240) %>%
  distinct(trip_haul_ID, .keep_all = TRUE)

#WINTER FLOUNDER
winterfl_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 106 & NESPP4 == 1200) %>%
  distinct(trip_haul_ID, .keep_all = TRUE)

#MONKFISH
monkfish_paired_tows_5mi_72hr_ob_re <- paired_tows_5mi_72hr_ob_re %>%
  filter(SVSPP == 197 & NESPP4 == 124) %>%
  distinct(trip_haul_ID, .keep_all = TRUE)
```


## Function Creation 
```{r}
#################### FUNCTIONS FOR T-TESTS ####################################
#plots to check for normality before t-tests 
#boxplot of catch per unit area
box.plot <- function(x) {
  x %>% 
  pivot_longer(cols = c(ob_species_cpua, nefsc_species_cpua), 
               names_to = "Trawl", 
               values_to = "CPUA") %>%
  filter(CPUA < 10000) %>%
  ggplot() + 
  geom_boxplot(aes(x = Trawl, y = CPUA)) + 
  labs(x = "Trawl Type") + 
  scale_x_discrete(labels = c("nefsc_species_cpua" = "NEFSC", 
                              "ob_species_cpua" = "Study Fleet")) + 
  theme_classic()
}

#histogram of catch per unit area
hist_kh <- function(x) {
  x %>%  
  ggplot() + 
  geom_histogram(aes(x = ob_species_cpua, y = ..density..), fill = "red") + 
  geom_label(aes(x = Inf, y = Inf, label = "Observer CPUE", vjust =1 , hjust = 1), color = "red") +
  geom_histogram(aes(x = nefsc_species_cpua, y = -..density..), fill = "blue") + 
  geom_label(aes(x = Inf, y = -Inf, label = "NEFSC CPUE", vjust = -1, hjust = 1), color = "blue") +
  labs(x = "CPUA (lb/min)", y = "Density", 
       title = "Histogram of CPUE for x", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  theme_classic()
}
  

#boxplot with log-transformed data 
box.log.plot <- function(x) {
  x %>% 
  pivot_longer(cols = c(log_ob_species_cpua, log_nefsc_species_cpua), 
               names_to = "Trawl", 
               values_to = "CPUA") %>%
  filter(CPUA < 10000) %>%
  ggplot() + 
  geom_boxplot(aes(x = Trawl, y = CPUA)) + 
  labs(x = "Trawl Type", y = "Log(CPUA)") + 
  scale_x_discrete(labels = c("log_nefsc_species_cpua" = "NEFSC", 
                              "log_ob_species_cpua" = "Observer")) + 
  theme_classic()
}

#histogram with log-transformed data 
hist_log_kh <- function(x) {
  x %>%  
  ggplot() + 
  geom_histogram(aes(x = log_ob_species_cpua, y = ..density..), fill = "red") + 
  # geom_label(aes(x = Inf, y = Inf, label = "Study Fleet CPUE", vjust =1 , hjust = 1), color = "red") +
  geom_histogram(aes(x = log_nefsc_species_cpua, y = -..density..), fill = "blue") + 
  # geom_label(aes(x = Inf, y = -Inf, label = "NEFSC CPUE", vjust = -1, hjust = 1), color = "blue") +
  labs(x = "Log(CPUA (lb/min))", y = "Density", 
       title = "Histogram of CPUE for x", 
       subtitle = "Pairs within 5 mi and 72 hrs") + 
  theme_classic()
}



######################## FUNCTIONS FOR MODELLING #############################
#trying to  create functions because I will be running the same models for every species dataset 
covars <- c("season", "mgmt_area", "trawl_type",  "VESSELNAME", "AVGDEPTH", "SURFTEMP", "BOTTEMP")
combos <- purrr::map(1:7, ~as.data.frame(t(combn(covars, .x))))

formulae <- combos %>%
  map_dfr(unite, col="formula", sep = " + ") %>%
  mutate(formula = paste0("relative_efficiency ~  ", formula))


#fit models (takes dataset)
fit.models <- function(x) {
  formulae$formula %>% purrr::map( ~glm(.x, family = binomial, data=x))
}


#compare models (takes list of models created by fit.models())
compare.models <- function(x) {
  formulae %>%
  mutate(aic =  purrr::map_dbl(x, AIC)) %>%
  arrange(desc(aic)) %>%
  mutate(deltaAIC = aic - aic[127]) %>%
  mutate(rsq =  purrr::map_dbl(x, Dsquared)) %>% 
  mutate(rsq = sprintf("%0.2f", rsq)) %>%
  mutate(aic = sprintf("%1.0f", aic)) %>%
  mutate(deltaAIC = sprintf("%1.0f", deltaAIC)) %>%
  kbl(col.names = (c("Model", "AIC", "deltaAIC","Deviance Explained"))) %>%
  kable_classic("striped", full_width = FALSE)
}


```



# Statisitical Analysis by Species 
## Cod
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(cod_paired_tows_5mi_72hr_ob_re)
hist_kh(cod_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
cod_paired_tows_5mi_72hr_ob_re <- cod_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(cod_paired_tows_5mi_72hr_ob_re)
hist_log_kh(cod_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data
cod_ttest <- t.test(cod_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, cod_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
cod_ttest


#back transform the estimate

```

#### Model Run 
```{r}
#COD
codm <- fit.models(cod_paired_tows_5mi_72hr_ob_re)

compare.models(codm)


#storing the optimal model and plotting the diagnostics
codm_ob_optimal <- glm(relative_efficiency ~ trawl_type + AVGDEPTH, family = binomial, data = cod_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(codm_ob_optimal)

summary(codm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(codm_ob_optimal), confint(codm_ob_optimal)))
```

## Haddock
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(haddock_paired_tows_5mi_72hr_ob_re)
hist_kh(haddock_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
haddock_paired_tows_5mi_72hr_ob_re <- haddock_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(haddock_paired_tows_5mi_72hr_ob_re)
hist_log_kh(haddock_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

haddock_ttest <- t.test(haddock_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, haddock_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
haddock_ttest


#back transform the estimate

```

#### Model Run 
```{r}
#HADDOCK
haddockm <- fit.models(haddock_paired_tows_5mi_72hr_ob_re)

compare.models(haddockm)


#storing the optimal model and plotting the diagnostics
haddockm_ob_optimal <- glm(relative_efficiency ~ mgmt_area + trawl_type + AVGDEPTH + BOTTEMP, family = binomial, data = haddock_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(haddockm_ob_optimal)

summary(haddockm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(haddockm_ob_optimal), confint(haddockm_ob_optimal)))
```

## Witch Flounder
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(witchfl_paired_tows_5mi_72hr_ob_re)
hist_kh(witchfl_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
witchfl_paired_tows_5mi_72hr_ob_re <- witchfl_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(witchfl_paired_tows_5mi_72hr_ob_re)
hist_log_kh(witchfl_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

witchfl_ttest <- t.test(witchfl_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, witchfl_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
witchfl_ttest

#back transform the estimate

```

#### Model Run 
```{r}
#WITCH FLOUNDER 
witchflm <- fit.models(witchfl_paired_tows_5mi_72hr_ob_re)

compare.models(witchflm)


#storing the optimal model and plotting the diagnostics
witchflm_ob_optimal <- glm(relative_efficiency ~ trawl_type, family = binomial, data = witchfl_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(witchflm_ob_optimal)

summary(witchflm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(witchflm_ob_optimal), confint(witchflm_ob_optimal)))

```

## Yewllowtail Flounder
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(yellowtailfl_paired_tows_5mi_72hr_ob_re)
hist_kh(yellowtailfl_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
yellowtailfl_paired_tows_5mi_72hr_ob_re <- yellowtailfl_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(yellowtailfl_paired_tows_5mi_72hr_ob_re)
hist_log_kh(yellowtailfl_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

yellowtail_ttest <- t.test(yellowtailfl_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, yellowtailfl_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
yellowtail_ttest


#back transform the estimate

```

#### Model Run 
```{r}
#YELLOWTAIL FLOUNDER
yellowtailflm <- fit.models(yellowtailfl_paired_tows_5mi_72hr_ob_re)

compare.models(yellowtailflm)


#storing the optimal model and plotting the diagnostics
yellowtailflm_ob_optimal <- glm(relative_efficiency ~ trawl_type, family = binomial, data = yellowtailfl_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(yellowtailflm_ob_optimal)

summary(yellowtailflm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(yellowtailflm_ob_optimal), confint(yellowtailflm_ob_optimal)))
```

## American Plaice
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(plaice_paired_tows_5mi_72hr_ob_re)
hist_kh(plaice_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
plaice_paired_tows_5mi_72hr_ob_re <- plaice_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(plaice_paired_tows_5mi_72hr_ob_re)
hist_log_kh(plaice_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

plaice_ttest <- t.test(plaice_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, plaice_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
plaice_ttest


#back transform the estimate

```

#### Model Run 
```{r}
#AMERICAN PLAICE 
plaicem <- fit.models(plaice_paired_tows_5mi_72hr_ob_re)

compare.models(plaicem)


#storing the optimal model and plotting the diagnostics
plaicem_ob_optimal <- glm(relative_efficiency ~ trawl_type, family = binomial, data = plaice_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(plaicem_ob_optimal)

summary(plaicem_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(plaicem_ob_optimal), confint(plaicem_ob_optimal)))

```

## Winter Flounder
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(winterfl_paired_tows_5mi_72hr_ob_re)
hist_kh(winterfl_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
winterfl_paired_tows_5mi_72hr_ob_re <- winterfl_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(winterfl_paired_tows_5mi_72hr_ob_re)
hist_log_kh(winterfl_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

winterfl_ttest <- t.test(winterfl_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, winterfl_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
winterfl_ttest


#back transform the estimate

```

#### Model Run 
```{r}
#WINTER FLOUNDER 
winterflm <- fit.models(winterfl_paired_tows_5mi_72hr_ob_re)

compare.models(winterflm)


#storing the optimal model and plotting the diagnostics
winterflm_ob_optimal <- glm(relative_efficiency ~ season + trawl_type + SURFTEMP, family = binomial, data = winterfl_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(winterflm_ob_optimal)

summary(winterflm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(winterflm_ob_optimal), confint(winterflm_ob_optimal)))

```

## Monkfish 
#### T-test
```{r}
#looking at the boxplot and histograms of the catch per unit area 
box.plot(monkfish_paired_tows_5mi_72hr_ob_re)
hist_kh(monkfish_paired_tows_5mi_72hr_ob_re)

#log-transforming the data
monkfish_paired_tows_5mi_72hr_ob_re <- monkfish_paired_tows_5mi_72hr_ob_re %>%
  mutate(log_ob_species_cpua = log(ob_species_cpua), 
         log_nefsc_species_cpua = log(nefsc_species_cpua))

#looking at the boxplot and histograms of the log(catch per unit area)
box.log.plot(monkfish_paired_tows_5mi_72hr_ob_re)
hist_log_kh(monkfish_paired_tows_5mi_72hr_ob_re)

#assumptions of normality and equal variance are met with the log transformed data, 
#so the t-test was conducted with the log-transformed data

monkfish_ttest <- t.test(monkfish_paired_tows_5mi_72hr_ob_re$log_ob_species_cpua, monkfish_paired_tows_5mi_72hr_ob_re$log_nefsc_species_cpua, paired = TRUE)
monkfish_ttest

#back transform the estimate


```

#### Model Run 
```{r}
#MONKFISH 
monkfishm <- fit.models(monkfish_paired_tows_5mi_72hr_ob_re)

compare.models(monkfishm)


#storing the optimal model and plotting the diagnostics
monkfishm_ob_optimal <- glm(relative_efficiency ~ trawl_type + AVGDEPTH, family = binomial, data = monkfish_paired_tows_5mi_72hr_ob_re)

par(mfrow=c(2,2))
plot(monkfishm_ob_optimal)

summary(monkfishm_ob_optimal)

#back transform the estimates into an odds-ratio 
exp(cbind(OR = coef(monkfishm_ob_optimal), confint(monkfishm_ob_optimal)))

```

# Playing Around 
```{r, eval=FALSE}
#COD
cod_paired_tows_5mi_72hr_ob_re
codm_ob_optimal


cod_paired_tows_5mi_72hr_ob_re %>%
  ggplot() + 
  geom_boxplot(aes(y = relative_efficiency, x = trawl_type))


codm_ob_optimal_p <- predict.glm(codm_ob_optimal)

effect_plot(codm_ob_optimal, pred = trawl_type, interval = TRUE, 
            plot.points = TRUE, jitter = 0.05)



cod_paired_tows_5mi_72hr_ob_re %>%
  ggplot() + 
  geom_point(aes(x = cod_paired_tows_5mi_72hr_ob_re$relative_efficiency,
                 y = predict(codm_ob_optimal), shape = trawl_type)) + 
  scale_shape_discrete(name = "Trawl Category", 
                       labels = c("Generic Groundfish Trawls", 
                                  "Flatfish Trawls", 
                                  "Separator Trawls",
                                  "Other/Unknown Trawls")) + 
  labs(x = "Actual Values", y = "Predicted Values") + 
  theme_classic()
  


cod_paired_tows_5mi_72hr_ob_re %>%
  ggplot() + 
  geom_point(aes(x = relative_efficiency,
                 y = predict(codm_ob_optimal), shape = trawl_type)) + 
  labs(title = "Predicted v Actual Values", 
       subtitle = "Cod - Pairs within 5 mi and 72 hrs",
       x = "Actual Values", y = "Predicted Values") + 
  facet_wrap(~ trawl_type, 
             labeller = as_labeller(c("1" = "Generic Groundfish Trawls", 
                                      "2" = "Flatfish Trawls", 
                                      "3" = "Separator Trawls",
                                      "5" = "Other/Unknown Trawls"))) + 
  guides(shape = FALSE) + 
  theme_classic() 

  

```

